### 2019-04-16 sample-sigconf.tex
Initial Overleaf Import

%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf,review, anonymous]{acmart}
\usepackage{float}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn

%
% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

% Rights management information. 
% This information is sent to you when you complete the rights form.
% These commands have SAMPLE values in them; it is your responsibility as an author to replace
% the commands and values with those provided to you when you complete the rights form.
%
% These commands are for a PROCEEDINGS abstract or paper.
\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmlicensed}

\acmConference[ESEC/FSE 2019]{The 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{26--30 August, 2019}{Tallinn, Estonia}

%
% These commands are for a JOURNAL article.
%\setcopyright{acmcopyright}
%\acmJournal{TOG}
%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
%\acmDOI{10.1145/1122445.1122456}

%
% Submission ID. 
% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
% of the event, and this ID should be used as the parameter to this command.
%\acmSubmissionID{123-A56-BU3}

%
% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
% the next command will enable that style.
%\citestyle{acmauthoryear}

%
% end of the preamble, start of the body of the document source.
\begin{document}

%
% The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
\title{Proposing Software Clusterings using Vector Semantics and the Call Graph: A Study on the Linux Kernel}

%
% The "author" command and its associated commands are used to define the authors and their affiliations.
% Of note is the shared affiliation of the first two authors, and the "authornote" and "authornotemark" commands
% used to denote shared contribution to the research.
\author{Marios Papachristou}

\email{papachristoumarios@gmail.com}
\affiliation{%
  \institution{National Technical University of Athens}
  \streetaddress{Zografou Campus}
  \city{Athens}
  \state{Attica}
  \postcode{157 73}
}

%
% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
% other information printed in the page headers. This command allows the author to define a more concise list
% of authors' names for this purpose.
\renewcommand{\shortauthors}{Papachristou}

\begin{abstract}

\noindent \textbf{Purpose -- } Propose a method to determine a software's modules without 
knowledge of its structure, and empirically validate the method's performance.

\noindent \textbf{Method -- } Cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the call graph, provided by Static Graph Analyzers to an augmented graph.
Use of the \emph{Louvain Algorithm} to iteratively exhibit its community structure and propose a module--level clustering.

\noindent \textbf{Results --} Our method performs better in terms of stability, authoritativeness 
and extremity over other state-of-the-art clustering methods proposed in literature and is able to decently 
recover the ground truth clustering of the Linux Kernel.

\noindent \textbf{Conclusions --} Semantic information from vector semantics and the call graph can produce 
accurate results for software clusterings of large systems.

\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10010147.10010257.10010258.10010260.10003697</concept_id>
<concept_desc>Computing methodologies~Cluster analysis</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010147.10010257.10010321</concept_id>
<concept_desc>Computing methodologies~Machine learning algorithms</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10010940.10010971.10010972</concept_id>
<concept_desc>Software and its engineering~Software architectures</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Cluster analysis}
\ccsdesc[500]{Computing methodologies~Machine learning algorithms}
\ccsdesc[500]{Software and its engineering~Software architectures}
%
% Keywords. The author(s) should pick words that accurately describe the work being
% presented. Separate the keywords with commas.
\keywords{document embeddings, doc2vec, linux kernel, natural language processing, software architecture recovery, software clustering, static graph analysis, vector semantics}

\maketitle

\section{Introduction}

Modern software systems usually span hundreds of thousands of source code lines (SLOC) 
since the inherent complexity of modern applications that computers have to solve has 
exponentially increased. The need for adoption of modular software architectural schemas 
becomes inevident for robust maintainability of the overall software system.
Since the architecture of a software system is the most fundamental realization of a 
software system, when there is no description of the architecture of it, software 
architects usually make attempts to recover it. In the past, there have been attempts to 
identify the main components of a software system using hierarchical clustering 
algorithms \cite{maqbool_overview} mainly by clustering modules into subsystems, given 
its source code.

Plenty of attention has been gathering around the variety of possibilities enabled by 
modern machine learning techniques and practices in Natural Language Processing (NLP) 
field and bought to the forefront by numerous open-source NLP projects, such as spaCy 
\cite{spacy} and NLTK \cite{nltk}, performing analysis on large corpuses of data. These 
practices can also be applied on codebases as corpuses of text, thus enabling researchers 
to extract useful information for the linguistic contents of the source codebase 
inaugurating new modes of reviewing large amounts of source code. So far, NLP practices 
have been a subject to systematic research for codebases, one attempt of them being the 
Deep Code Search project \cite{deepcodesearch}.

This paper aims to propose software clusterings using a combination of vector semantics on the source code provided by \emph{Doc2Vec} as well as the existing structure of 
the codebase via the call graph in order to construct an augmented call graph and form communities in this graph ariving at a module--level 
architecture viewed from the call graph perspective. Our approach will be applied on the 
Linux Kernel codebase and will be compared to its existing layered architecture using 
MoJo distance as a clusterings metric, proposed by Tzerpos and Holt in reference \cite{mojo}, 
as well as, compare its stability and extremity compared to other Clustering 
Algorithms that exist in literature.

% XXX Not sure if needed

% We begin with a brief outline of the theoretical background concerning layered 
% architectures addressing its conjunction with software analysis tools and NLP practices. 
% Next, we propose methods for analyzing large codebases using techniques outlined in the 
% Methodology section. Next, we present the case study of analyzing the Linux Kernel 
% codebase using certain evaluation criteria, as well as results induced by the methodology 
% we have proposed. Finally, conclude and recommend roadmaps for future research on the 
% topic.

\section{Method}

\paragraph{Embeddings}

For the preprocessing stage use the NLP package spaCy \cite{spacy} which provided us with very useful tools for the extraction. After preprocessing, we use gensim \cite{gensim} to train the Doc2Vec model. First of all, we remove the stopwords that occured in the text like control flow keywords like \texttt{if}, semicolons, variable types like \texttt{int} and so on. Next, we tokenize each word splitting it to its constituent parts regarding its form. For example the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}. Then the identifiers are split using a dynamic programming approach, so the identifier \texttt{inprogress} is split into \texttt{in} and \texttt{progress}. Then we pass the tokens from an English lemmatizer to remove excess information for words. For example a token for an array named \texttt{literals} becomes \texttt{literal}. After that, the vector size for the Doc2Vec algorithm is set according to the size of the codebase which is being examined each time, in the order of magnitude of a few hundreds since for smaller datasets with poorer vocabularies, a lower dimension
should suffice for capturing the necessary features.  Finally, the document tags corresponded to the source code files or modules and the algorithm are assigned a vector $\vec u_v \in \mathbb R^d$ for each $v \in V$.

% The identifier \texttt{inprogress} should be split into \texttt{in} and \texttt{progress} 
% which provides us with a more meaningful content for the word embeddings from a 
% linguistic point of view. The identifier segmentation problem is reduced to using an arbitrary number of separators we must split the identifier $s = i_1 i_2 \dots i_n$ such
% that the total cost of splitting such words minimizing the split cost. Using a word-level $n$-gram model we define the cost function of a (sub)-word $s_k$ given prior words $s_{k-1}, s_{k-2} \dots, s_{k-n + 1}$ and a dataset $\mathcal D$ as $c(s_k | s_{k-1} \dots s_{k - n + 1}, \mathcal D) = - \log \hat p_{MLE} (s_k | s_{k-1} \dots s_{k-n+1}, \mathcal D)$ where $\hat p_{MLE} (\cdot)$ is the Maximum Likelihood Estimator of the event. Let $L(m)$ be the cost of the optimal split in the $m$ character of the identifier. Then

% $$L(m) = 
% \begin{cases}
% 	\min_{0 \le \ell < m} \{ L(\ell) + c(s[\ell:m]  \mid \\ \text{ prior words to } s% [\ell:m] ) \} & 1 \le m \le |s| \\
%	0 & m = 0

%\end{cases}
%$$

\paragraph{Call Graph Generation} The codebase is processed by a Static Graph Analyzer. In our approach, focusing on C projects, we use \emph{CScout} \cite{cscout} in order to generate the directed call graph. Each source code file is assigned to a module. Modules can be user defined or automatically generated by their respective directories at a desired directory tree depth.

\paragraph{Combining semantics and the Call Graph} The input to the clustering procedure
 is the call graph with cosine similarities of the various modules as weights, thus forming a
  weighted directed graph. Then we run the Louvain Clustering Algorithm \cite{louvain} in
   order to obtain the software clustering via maximizing the modularity function with a
    greedy approach. Further refining can also be done by re-running the algorithm on the contracted graph with mean embeddings as embeddings for each node.

\paragraph{Implementation}  Our method is implemented in the Python Language using spaCy\cite{spacy} for the 
NLP tasks, Gensim \cite{gensim} for the generation of Document Embeddings. The library 
used to handle graphs and graph operations was NetworkX \cite{nx}. The code is available on GitHub.

\paragraph{Decision Rationale for Evaluation System} We have chosen to use the Linux Kernel as a codebase to evaluate our method on since it is a large and complex system with 27 years of continuous development, spanning 20.3 millions SLOC at the time of writing.  Moreover, it is easy to find ground truth system due to its clear directory structure and construct testcases for
evaluations. Finally, it was also used in related studies \cite{acdc, evaluation} as a reference system for evaluation.

\paragraph{Experimental Setting} Our method was run on the Linux Kernel 4.21,
 consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} and Ward-Linkage \cite{ward} as well as ACDC and LIMBO. The results are presented in Table \ref{table:evaluation}. As ground truth we have used the first level directories as a target clustering and as input we have considered the modules of the one-top directories. For example, the source code file \texttt{drivers/net/ieee802154/mcr20a.c} has a ground truth value of \texttt{drivers} and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. As a clustering distance metric we have used the MoJo metric, as proposed in reference \cite{mojo}. Since, Louvain Community Detection produces 
 different (but very similar) results every time it runs, we ran the simulations multiple times and averaged the results.

\section{Discussion of Results}

 In Table \ref{tab:evaluation}, there are the results of the clusterings ordered in increasing MoJo distance with respect to the Ground Truth. We have included the number of clusters produced, the cluster size range, the average cluster size the standard deviation in the cluster sizes, the median cluster and the MoJo distances with respect to the ground truth. The Ground Truth clustering is also present in the table. Our quality metrics for the clusterings are 
\emph{extremity}, \emph{authoritativeness} and \emph{stability} as proposed in reference \cite{evaluation}

Firstly, our approach produced balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, producing an amount of clusters that was close to the Ground Truth with smaller standard deviation in the cluster sizes than the other clustering methods, without knowing the number of clusters \emph{a priori}. Besides this, our approach also seems to give balanced clusters with respect to \emph{Median Cluster} criterion. Note that ACDC, which took into account only the structural properties of the files, produced a high granularity clustering that failed to catch the structure of the Linux Kernel Codebase.

Moreover, in the \emph{authoritativeness} criterion, our approach outperformed the other clusterings to a very up to 10 times in terms of MoJo distance being very close (smaller is better) to the Ground Truth, with a very small standard deviation. This also suggests great
\emph{stability} in the resulting clusterings. Note that the other clustering methods we compared against ours gave disappointing MoJo distances even with their cluster number defined 
equal to the one of the Ground Truth.

\section{Related Work}

% TODO Needs review

% The architecture of a software system is a \emph{"living organism"} meaning that it is 
% changing constantly over time, even for small projects. The evolution software 
% architecture may lead to architectural decay \cite{large_study}. The identification of such 
% a decay is non-trivial and requires a large amount of effort and understanding of the 
% software system in order to be diagnosed.

% Architectural recovery is an active research 
%field aiming to make software systems more understandable and maintainable over time. The 
%study of architectural change requires that the architecture at a given point in time, 
%for example after a major release, during a system's evolution must be inferred. 
Various algorithms have been proposed for realizing architectural schemata many of which use 
different features for describing the source code.

Onaiza Maqbool and Haroon A. Babri \cite{maqbool_overview} present an
overview of the various approaches taken towards to hierarchical clustering algorithms
for software systems. In their study, they compare the various clustering algorithms
such as ACDC, LIMBO and other Traditional Clustering Algorithms such as Single
Linkage, Complete Linkage \cite{complete} and Weighted Linkage presenting their efficiency regarding 
multiple feature sets.

Added to this, a \emph{semantics-based architectural view} of the system, as discussed in reference
\cite{large_study} reveals significant aspects of a software system and its change over 
time, which suggests that semantic-based approached should be followed for gaining better 
understandings of a software system. Their suggestion is a \emph{term frequency--inverse 
document frequency} (TF-IDF) model serving as a similarity metric between source code 
entities.

Work in Software Clustering Algorithms (SCA) has been extensively done by Tzerpos in
references \cite{MoJoFM}, \cite{stability}, \cite{acdc} and \cite{limbo} with the ACDC
and LIMBO clustering algorithms.

In particular, the ACDC algorithm leans toward to software components comprehension 
based on subsystem patterns. Their approach considers an initial structure of the system, without taking into account semantics, and tries to build comprehensive clusterings of the given ground structure. The authors also conducted a study on an older version of  the Linux Kernel.

Finally, Andritsos and Tzerpos in research article \cite{limbo} present an Information--Theoretic 
approach of SCA by developing LIMBO which clusters modules upon inserting their Distributional Cluster Features to a B-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm, merging the clusters with the minimum mutual information loss together.

\section{Conclusions} This paper is set out to show how we can use a combination of vector semantics
and information from the call graph in order to produce meaningful clusterings of a software system.

Taking into consideration the trends and trajectories of modern software architecture recovery techniques, we have conducted our study in a huge codebase spanning 20.3 millions of SLOC and we have outperformed
several clustering algorithms of the existing literature in terms of \emph{extremity} and \emph{authoritativeness} as well as we have produced \emph{stable} clusterings of the codebase 
without even the knowledge of the number of clusters of the Ground Truth. This evidence strongly
supports the further usage of vector semantics and structural information of the project for the 
recovery of the underlying architecture of a software system.

Within the context of this project further work is encouraged in several areas such identifier splitting, 
which can be done using deep learning \cite{splitting}, integration with more static analyzers and usage 
of the project in order to propose layered architectures by finding tree structures on the resulting clustering. 
Finally, it is  encouraged to try other methods described thoroughly in \cite{malliaros}, such as using a 
different modularity function or using spectral clustering and cut-based measures.

\begin{table*}
  \caption{Experimental Results for the Linux Kernel 4.21 Codebase}
    \label{tab:evaluation}
    \begin{tabular}{lrrrrrr}
    \toprule
    Algorithm & Number of Clusters & Cluster Size Range & Avg. Cluster & Standard Deviation & Median Cluster & MoJo Distance \\
    \midrule
    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 4.53 & 45.82 & 2\\
    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725.11 & 1 & 2092 \\
    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412.34 & 19.0 & 1710 \\
    LIMBO \cite{limbo} & & \\
    SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
    SADE (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\

    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70.0 & 1138 \\
    Ground Truth & 21 & 1--1348 & 163 & 340.62 & 11.0 & -- \\
    \bottomrule
  \end{tabular}
\end{table*}

\newpage
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

\end{document}

### 2019-04-26 manuscript/manuscript.tex
Move manuscript under manuscript/ directory

--- 2019-04-16 sample-sigconf.tex
@@
 % The "title" command has an optional parameter, allowing the author to define a "short title" to be used in page headers.
-\title{Proposing Software Clusterings using Vector Semantics and the Call Graph: A Study on the Linux Kernel}
+\title{Software Clusterings with Vector Semantics and 
+the Call Graph}
 
@@
 \noindent \textbf{Purpose -- } Propose a method to determine a software's modules without 
-knowledge of its structure, and empirically validate the method's performance.
+knowledge of its architectural structure, and empirically validate the method's performance.
 
@@
 
-Modern software systems usually span hundreds of thousands of source code lines (SLOC) 
-since the inherent complexity of modern applications that computers have to solve has 
-exponentially increased. The need for adoption of modular software architectural schemas 
+%Modern software systems usually span hundreds of thousands of source code lines (SLOC) 
+%since the inherent complexity of modern applications that computers have to solve has 
+%exponentially increased.
+
+In modern software systems, the need for adoption of modular software architectural schemas 
 becomes inevident for robust maintainability of the overall software system.
@@
 identify the main components of a software system using hierarchical clustering 
-algorithms \cite{maqbool_overview} mainly by clustering modules into subsystems, given 
+algorithms \cite{maqbool_overview, limbo} mainly by clustering modules into subsystems, given 
 its source code.    
-
-Plenty of attention has been gathering around the variety of possibilities enabled by 
-modern machine learning techniques and practices in Natural Language Processing (NLP) 
-field and bought to the forefront by numerous open-source NLP projects, such as spaCy 
-\cite{spacy} and NLTK \cite{nltk}, performing analysis on large corpuses of data. These 
-practices can also be applied on codebases as corpuses of text, thus enabling researchers 
-to extract useful information for the linguistic contents of the source codebase 
-inaugurating new modes of reviewing large amounts of source code. So far, NLP practices 
-have been a subject to systematic research for codebases, one attempt of them being the 
-Deep Code Search project \cite{deepcodesearch}.
+The possibilities offered by machine learning techniques and practices in the Natural Language Processing (NLP) 
+can also be applied on codebases as corpuses of text, thus enabling 
+the extraction of useful information for the semantics of the source codebase 
+inaugurating new modes of reviewing large amounts of source code.
+An example is demonstrated through the Deep Code Search Project \cite{deepcodesearch} .
 
 This paper aims to propose software clusterings using a combination of vector semantics on the source code provided by \emph{Doc2Vec} as well as the existing structure of 
-the codebase via the call graph in order to construct an augmented call graph and form communities in this graph ariving at a module--level 
-architecture viewed from the call graph perspective. Our approach will be applied on the 
-Linux Kernel codebase and will be compared to its existing layered architecture using 
-MoJo distance as a clusterings metric, proposed by Tzerpos and Holt in reference \cite{mojo}, 
-as well as, compare its stability and extremity compared to other Clustering 
-Algorithms that exist in literature.
+the codebase via the call graph in order to form communities adn arrive at a module-level 
+architecture viewed from the call graph perspective. 
+We will study Linux codebase and we will compare it with ground truth in using the MoJo metric \cite{mojo} as well as 
+compare it with other state-of-the-art and baseline clustering algorithms \cite{maqbool_overview, evaluation} in terms of 
+\emph{stability}, \emph{authoritativeness} and \emph{extremity}
 
@@
 
+\begin{table*}
+  \caption{Experimental Results for Linux 4.21 Codebase}
+    \label{tab:evaluation}
+    \begin{tabular}{lrrrrrr}
+    \toprule
+    Algorithm & Number of Clusters & Cluster Size Range & Avg. Cluster & Standard Deviation & Median Cluster & MoJo Distance \\
+    \midrule
+    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 4.53 & 45.82 & 2\\
+    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725.11 & 1 & 2092 \\
+    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412.34 & 19.0 & 1710 \\
+    LIMBO \cite{limbo} & & \\
+    SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
+    SADE (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
+
+    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70.0 & 1138 \\
+    Ground Truth & 21 & 1--1348 & 163 & 340.62 & 11.0 & -- \\
+    \bottomrule
+  \end{tabular}
+\end{table*}
+
 \paragraph{Embeddings}
@@
 After preprocessing, we use gensim \cite{gensim} to train the Doc2Vec model.
-First of all, we remove the stopwords that occured in the text like control flow keywords like \texttt{if}, semicolons, variable types like \texttt{int} and so on.
-Next, we tokenize each word splitting it to its constituent parts regarding its form.
-For example the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}.
-Then the identifiers are split using a dynamic programming approach, so the identifier \texttt{inprogress} is split into \texttt{in} and \texttt{progress}.
-Then we pass the tokens from an English lemmatizer to remove excess information for words.
-For example a token for an array named \texttt{literals} becomes \texttt{literal}.
-After that, the vector size for the Doc2Vec algorithm is set according to the size of the codebase which is being examined each time, in the order of magnitude of a few hundreds since for smaller datasets with poorer vocabularies, a lower dimension
-should suffice for capturing the necessary features.
-Finally, the document tags corresponded to the source code files or modules and the algorithm are assigned a vector $\vec u_v \in \mathbb R^d$ for each $v \in V$.
+First of all, we tokenize the code and remove the stopwords.
+After that, for each token, we split it into its constituent parts using dynamic programming and lemmatize
+each individual sub-token. 
+For example the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, \texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.
 
@@
    order to obtain the software clustering via maximizing the modularity function with a
-    greedy approach. Further refining can also be done by re-running the algorithm on the contracted graph with mean embeddings as embeddings for each node.
+    greedy approach.
 
-\paragraph{Implementation}  Our method is implemented in the Python Language using spaCy\cite{spacy} for the 
-NLP tasks, Gensim \cite{gensim} for the generation of Document Embeddings. The library 
-used to handle graphs and graph operations was NetworkX \cite{nx}. The code is available on GitHub.
+    %Further refining can also be done by re-running the algorithm on the contracted graph with mean embeddings as embeddings for each node.
 
-\paragraph{Decision Rationale for Evaluation System} We have chosen to use the Linux Kernel as a codebase to evaluate our method on since it is a large and complex system with 27 years of continuous development, spanning 20.3 millions SLOC at the time of writing.
+\paragraph{Implementation}  Our method is implemented in the Python Language using spaCy\cite{spacy} Gensim \cite{gensim} and NetworkX \cite{nx}.
+
+% used to handle graphs and graph operations was NetworkX \cite{nx}. The code is available on GitHub.
+
+\paragraph{Decision Rationale for Evaluation System} We have chosen to use Linux as a codebase to evaluate our method on since it is a large and complex system with 27 years of continuous development, spanning 20.3 millions SLOC at the time of writing.
 Moreover, it is easy to find ground truth system due to its clear directory structure and construct testcases for
@@
 
-\paragraph{Experimental Setting} Our method was run on the Linux Kernel 4.21,
+\paragraph{Experimental Setting} Our method was run on Linux 4.21,
  consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} and Ward-Linkage \cite{ward} as well as ACDC and LIMBO.
-The results are presented in Table \ref{table:evaluation}.
+The results are presented in Table \ref{tab:evaluation}.
 As ground truth we have used the first level directories as a target clustering and as input we have considered the modules of the one-top directories.
@@
 
-\section{Discussion of Results}
+\section{Results, Evaluation, Discussion}
 
@@
 Besides this, our approach also seems to give balanced clusters with respect to \emph{Median Cluster} criterion.
-Note that ACDC, which took into account only the structural properties of the files, produced a high granularity clustering that failed to catch the structure of the Linux Kernel Codebase.
-
+Note that ACDC, which took into account only the structural properties of the files, produced a high granularity clustering that failed to catch the structure of Linux Codebase.
 Moreover, in the \emph{authoritativeness} criterion, our approach outperformed the other clusterings to a very up to 10 times in terms of MoJo distance being very close (smaller is better) to the Ground Truth, with a very small standard deviation.
@@
 %for example after a major release, during a system's evolution must be inferred. 
-Various algorithms have been proposed for realizing architectural schemata many of which use 
-different features for describing the source code.
+%Various algorithms have been proposed for realizing architectural schemata many of which use 
+%different features for describing the source code.
 
@@
 multiple feature sets. 
-
 Added to this, a \emph{semantics-based architectural view} of the system, as discussed in reference
@@
 entities. 
-
 Work in Software Clustering Algorithms (SCA) has been extensively done by Tzerpos in
-references \cite{MoJoFM}, \cite{stability}, \cite{acdc} and \cite{limbo} with the ACDC
+references \cite{mojo}, \cite{stability}, \cite{acdc} and \cite{limbo} with the ACDC
 and LIMBO clustering algorithms.
@@
 Their approach considers an initial structure of the system, without taking into account semantics, and tries to build comprehensive clusterings of the given ground structure.
-The authors also conducted a study on an older version of  the Linux Kernel.
-
-Finally, Andritsos and Tzerpos in research article \cite{limbo} present an Information--Theoretic 
-approach of SCA by developing LIMBO which clusters modules upon inserting their Distributional Cluster Features to a B-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm, merging the clusters with the minimum mutual information loss together.
+The authors also conducted a study on an older version of  Linux.
+Moreover, Andritsos and Tzerpos in reference \cite{limbo} present an Information--Theoretic 
+approach of SCA by developing LIMBO which clusters modules upon inserting their Distributional Cluster Features to a B+-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm, merging the clusters with the minimum mutual information loss together.
 
@@
 and information from the call graph in order to produce meaningful clusterings of a software system.
-
-Taking into consideration the trends and trajectories of modern software architecture recovery techniques, we have conducted our study in a huge codebase spanning 20.3 millions of SLOC and we have outperformed
-several clustering algorithms of the existing literature in terms of \emph{extremity} and \emph{authoritativeness} as well as we have produced \emph{stable} clusterings of the codebase 
-without even the knowledge of the number of clusters of the Ground Truth. This evidence strongly
-supports the further usage of vector semantics and structural information of the project for the 
-recovery of the underlying architecture of a software system.
-
-Within the context of this project further work is encouraged in several areas such identifier splitting, 
-which can be done using deep learning \cite{splitting}, integration with more static analyzers and usage 
-of the project in order to propose layered architectures by finding tree structures on the resulting clustering. 
-Finally, it is  encouraged to try other methods described thoroughly in \cite{malliaros}, such as using a 
-different modularity function or using spectral clustering and cut-based measures.
-
-\begin{table*}
-  \caption{Experimental Results for the Linux Kernel 4.21 Codebase}
-    \label{tab:evaluation}
-    \begin{tabular}{lrrrrrr}
-    \toprule
-    Algorithm & Number of Clusters & Cluster Size Range & Avg. Cluster & Standard Deviation & Median Cluster & MoJo Distance \\
-    \midrule
-    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 4.53 & 45.82 & 2\\
-    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725.11 & 1 & 2092 \\
-    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412.34 & 19.0 & 1710 \\
-    LIMBO \cite{limbo} & & \\
-    SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
-    SADE (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
-
-    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70.0 & 1138 \\
-    Ground Truth & 21 & 1--1348 & 163 & 340.62 & 11.0 & -- \\
-    \bottomrule
-  \end{tabular}
-\end{table*}
+We conclude that we have outperformed state-of-the-art software clusterings and conventional
+agglomerative clustering algorithms 
+in terms of \emph{extremity}, \emph{authoritativeness} and \emph{stability} 
+without knowing the number of clusters of the Ground Truth. This evidence strongly
+supports the further usage of vector semantics and the call graph for architecture recovery.
+Finally, further work is encouraged in several areas such as 
+integration with more static analyzers and use of the project in order to propose layered architectures.
 
@@
 \bibliographystyle{ACM-Reference-Format}
-\bibliography{sample-base}
+\bibliography{references}
 

### 2019-04-26 manuscript/manuscript.tex
Refactor manuscript and add ACDC MoJo Distance

@@
 
-In modern software systems, the need for adoption of modular software architectural schemas 
-becomes inevident for robust maintainability of the overall software system.
+In modern software systems, the need for adoption of modular software architectural schemata 
+becomes inevitable for robust maintainability of the overall software system.
 Since the architecture of a software system is the most fundamental realization of a 
@@
 The possibilities offered by machine learning techniques and practices in the Natural Language Processing (NLP) 
-can also be applied on codebases as corpuses of text, thus enabling 
+can also be applied on codebases as corpora of text, thus enabling 
 the extraction of useful information for the semantics of the source codebase 
@@
 
-This paper aims to propose software clusterings using a combination of vector semantics on the source code provided by \emph{Doc2Vec} as well as the existing structure of 
-the codebase via the call graph in order to form communities adn arrive at a module-level 
+This paper aims to propose software clusterings using a combination of vector semantics on the source code provided 
+by \emph{Doc2Vec} as well as the existing structure of 
+the codebase via the call graph in order to form communities and arrive at a module-level 
 architecture viewed from the call graph perspective. 
@@
 \emph{stability}, \emph{authoritativeness} and \emph{extremity}
-
-% XXX Not sure if needed
-
-% We begin with a brief outline of the theoretical background concerning layered 
-% architectures addressing its conjunction with software analysis tools and NLP practices. 
-% Next, we propose methods for analyzing large codebases using techniques outlined in the 
-% Methodology section. Next, we present the case study of analyzing the Linux Kernel 
-% codebase using certain evaluation criteria, as well as results induced by the methodology 
-% we have proposed. Finally, conclude and recommend roadmaps for future research on the 
-% topic.
 
@@
     \midrule
-    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 4.53 & 45.82 & 2\\
+    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 4.53 & 45.82 & 2 & 33694\\
     Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725.11 & 1 & 2092 \\
     Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412.34 & 19.0 & 1710 \\
-    LIMBO \cite{limbo} & & \\
+    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70.0 & 1138 \\
+
+    LIMBO \cite{limbo} & 21 & & \\
     SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
@@
 
-    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70.0 & 1138 \\
     Ground Truth & 21 & 1--1348 & 163 & 340.62 & 11.0 & -- \\
@@
 
-For the preprocessing stage use the NLP package spaCy \cite{spacy} which provided us with very useful tools for the extraction.
-After preprocessing, we use gensim \cite{gensim} to train the Doc2Vec model.
-First of all, we tokenize the code and remove the stopwords.
+For the prepossessing stage use the NLP package spaCy \cite{spacy} which provided us with very useful tools for the extraction. 
+After prepossessing, we use Gensim \cite{gensim} to train the Doc2Vec model. 
+First of all, we tokenize the code and remove the stop-words. 
 After that, for each token, we split it into its constituent parts using dynamic programming and lemmatize 
 each individual sub-token. 
-For example the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, \texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.
+For example the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, 
+\texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.
 
-% The identifier \texttt{inprogress} should be split into \texttt{in} and \texttt{progress} 
-% which provides us with a more meaningful content for the word embeddings from a 
-% linguistic point of view. The identifier segmentation problem is reduced to using an arbitrary number of separators we must split the identifier $s = i_1 i_2 \dots i_n$ such
-% that the total cost of splitting such words minimizing the split cost.
-Using a word-level $n$-gram model we define the cost function of a (sub)-word $s_k$ given prior words $s_{k-1}, s_{k-2} \dots, s_{k-n + 1}$ and a dataset $\mathcal D$ as $c(s_k | s_{k-1} \dots s_{k - n + 1}, \mathcal D) = - \log \hat p_{MLE} (s_k | s_{k-1} \dots s_{k-n+1}, \mathcal D)$ where $\hat p_{MLE} (\cdot)$ is the Maximum Likelihood Estimator of the event.
-Let $L(m)$ be the cost of the optimal split in the $m$ character of the identifier.
-Then
-
-% $$L(m) = 
-% \begin{cases}
-% 	\min_{0 \le \ell < m} \{ L(\ell) + c(s[\ell:m]  \mid \\ \text{ prior words to } s% [\ell:m] ) \} & 1 \le m \le |s| \\
-%	0 & m = 0
-
-%\end{cases}
-%$$
-
-\paragraph{Call Graph Generation} The codebase is processed by a Static Graph Analyzer.
+\paragraph{Call Graph Generation} 
+The codebase is processed by a Static Graph Analyzer. 
 In our approach, focusing on C projects, we use \emph{CScout} \cite{cscout} in order to generate the directed call graph. 
@@
 
-\paragraph{Combining semantics and the Call Graph} The input to the clustering procedure
+\paragraph{Combining semantics and the Call Graph} 
+The input to the clustering procedure
 is the call graph with cosine similarities of the various modules as weights, thus forming a
 weighted directed graph. Then we run the Louvain Clustering Algorithm \cite{louvain} in
-   order to obtain the software clustering via maximizing the modularity function with a
-    greedy approach.
+order to obtain the software clustering via maximizing the modularity function with a greedy approach. 
+In case we want to use edge directionality we do a bipartite transformation, detect communities and
+merge the results with a disjoint-set data structure.
 
-    %Further refining can also be done by re-running the algorithm on the contracted graph with mean embeddings as embeddings for each node.
+\paragraph{Implementation}  
+Our method is implemented in the Python Language using spaCy\cite{spacy} Gensim \cite{gensim} and NetworkX \cite{nx}.
 
-\paragraph{Implementation}  Our method is implemented in the Python Language using spaCy\cite{spacy} Gensim \cite{gensim} and NetworkX \cite{nx}.
-
-% used to handle graphs and graph operations was NetworkX \cite{nx}. The code is available on GitHub.
-
-\paragraph{Decision Rationale for Evaluation System} We have chosen to use Linux as a codebase to evaluate our method on since it is a large and complex system with 27 years of continuous development, spanning 20.3 millions SLOC at the time of writing.
-Moreover, it is easy to find ground truth system due to its clear directory structure and construct testcases for
-evaluations. Finally, it was also used in related studies \cite{acdc, evaluation} as a reference system for evaluation.
+\paragraph{Decision Rationale for Evaluation System} 
+We have chosen to use Linux as a codebase to evaluate our method on 
+since it is a large and complex system with 27 years of continuous development, spanning 20.3 millions source lines of code (SLOC) at the time of writing.  
+Moreover, it is easy to find ground truth system due to its clear directory structure and construct test-cases for
+evaluations. 
+Finally, it was also used in related studies \cite{acdc, evaluation} as a reference system for evaluation.
 
 \paragraph{Experimental Setting} Our method was run on Linux 4.21,
- consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} and Ward-Linkage \cite{ward} as well as ACDC and LIMBO.
-The results are presented in Table \ref{tab:evaluation}.
-As ground truth we have used the first level directories as a target clustering and as input we have considered the modules of the one-top directories.
-For example, the source code file \texttt{drivers/net/ieee802154/mcr20a.c} has a ground truth value of \texttt{drivers} and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}.
+consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
+and Ward-Linkage \cite{ward} as well as ACDC and LIMBO ($B = 10, S = \infty$). The results are presented in Table \ref{tab:evaluation}. 
+As ground truth we have used the first level directories as a target clustering and as input we have considered 
+the modules of the one-top directories. 
+For example, the source code file \texttt{drivers/net/ieee802154\-/mcr20a.c} has a ground truth value of \texttt{drivers} 
+and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. 
 As a clustering distance metric we have used the MoJo metric, as proposed in reference \cite{mojo}. 
-Since, Louvain Community Detection produces
- different (but very similar) results every time it runs, we ran the simulations multiple times and averaged the results.
+Since, Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
+multiple times and averaged the results.
 
-\section{Results, Evaluation, Discussion}
+\section{Results, Evaluation \& Discussion}
 
- In Table \ref{tab:evaluation}, there are the results of the clusterings ordered in increasing MoJo distance with respect to the Ground Truth.
-We have included the number of clusters produced, the cluster size range, the average cluster size the standard deviation in the cluster sizes, the median cluster and the MoJo distances with respect to the ground truth.
+In Table \ref{tab:evaluation}, there are the results of the clusterings ordered in increasing MoJo distance 
+with respect to the Ground Truth. 
+We have included the number of clusters produced, the cluster size range, the average cluster size the standard
+deviation in the cluster sizes, the median cluster and the MoJo distances with respect to the ground truth. 
 The Ground Truth clustering is also present in the table. 
@@
 
-Firstly, our approach produced balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, producing an amount of clusters that was close to the Ground Truth with smaller standard deviation in the cluster sizes than the other clustering methods, without knowing the number of clusters \emph{a priori}.
+Firstly, our approach produced balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, 
+producing an amount of clusters that was close to the Ground Truth with smaller standard deviation in the cluster sizes than 
+the other clustering methods, without knowing the number of clusters \emph{a priori}. 
 Besides this, our approach also seems to give balanced clusters with respect to \emph{Median Cluster} criterion. 
-Note that ACDC, which took into account only the structural properties of the files, produced a high granularity clustering that failed to catch the structure of Linux Codebase.
-Moreover, in the \emph{authoritativeness} criterion, our approach outperformed the other clusterings to a very up to 10 times in terms of MoJo distance being very close (smaller is better) to the Ground Truth, with a very small standard deviation.
-This also suggests great
-\emph{stability} in the resulting clusterings. Note that the other clustering methods we compared against ours gave disappointing MoJo distances even with their cluster number defined 
-equal to the one of the Ground Truth.
+Note that ACDC, which took into account only the structural properties of the files, produced a high 
+granularity clustering that failed to catch the structure of Linux Codebase. 
+Moreover, in the \emph{authoritativeness} criterion, our approach outperformed the other clusterings to a very up to 10 times 
+in terms of MoJo distance being very close (smaller is better) to the Ground Truth, with a very small standard deviation. 
+This also suggests great \emph{stability} in the resulting clusterings. 
+Note that the other clustering methods we compared against ours gave disappointing MoJo distances even with their cluster
+number defined equal to the one of the Ground Truth.
 
 \section{Related Work}
-
-% TODO Needs review
-
-% The architecture of a software system is a \emph{"living organism"} meaning that it is 
-% changing constantly over time, even for small projects. The evolution software 
-% architecture may lead to architectural decay \cite{large_study}. The identification of such 
-% a decay is non-trivial and requires a large amount of effort and understanding of the 
-% software system in order to be diagnosed.
-
-% Architectural recovery is an active research 
-%field aiming to make software systems more understandable and maintainable over time. The 
-%study of architectural change requires that the architecture at a given point in time, 
-%for example after a major release, during a system's evolution must be inferred. 
-%Various algorithms have been proposed for realizing architectural schemata many of which use 
-%different features for describing the source code.
 
@@
 In particular, the ACDC algorithm leans toward to software components comprehension 
-based on subsystem patterns.
-Their approach considers an initial structure of the system, without taking into account semantics, and tries to build comprehensive clusterings of the given ground structure.
+based on subsystem patterns. Their approach considers an initial structure of the system, 
+without taking into account semantics, and tries to build comprehensive clusterings of the given ground structure. 
 The authors also conducted a study on an older version of  Linux. 
 Moreover, Andritsos and Tzerpos in reference \cite{limbo} present an Information--Theoretic 
-approach of SCA by developing LIMBO which clusters modules upon inserting their Distributional Cluster Features to a B+-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm, merging the clusters with the minimum mutual information loss together.
+approach of SCA by developing LIMBO which clusters modules upon inserting their Distributional Cluster Features 
+to a B+-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm, merging the 
+clusters with the minimum mutual information loss together.
 

### 2019-04-26 manuscript/manuscript.tex
Add LIMBO results

@@
     \midrule
-    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 4.53 & 45.82 & 2 & 33694\\
-    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725.11 & 1 & 2092 \\
-    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412.34 & 19.0 & 1710 \\
-    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70.0 & 1138 \\
+    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
+    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725 & 1 & 2092 \\
+    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412 & 19.0 & 1710 \\
+    LIMBO \cite{limbo} & 21 & 50--1810 & 163 & 375 & 50  & 1482 \\
 
-    LIMBO \cite{limbo} & 21 & & \\
+    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70 & 1138 \\
+
     SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
     SADE (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
-
-    Ground Truth & 21 & 1--1348 & 163 & 340.62 & 11.0 & -- \\
+    \midrule
+    Ground Truth & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
     \bottomrule
@@
 consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
-and Ward-Linkage \cite{ward} as well as ACDC and LIMBO ($B = 10, S = \infty$). The results are presented in Table \ref{tab:evaluation}. 
+and Ward-Linkage \cite{ward} as well as ACDC and LIMBO with $B = 100$, $S = \infty$ and Bag-of-Words features. The results are presented in Table \ref{tab:evaluation}. 
 As ground truth we have used the first level directories as a target clustering and as input we have considered 

### 2019-04-27 manuscript/manuscript.tex

@@
 
-%
-% By default, the full list of authors will be used in the page headers. Often, this list is too long, and will overlap
-% other information printed in the page headers. This command allows the author to define a more concise list
-% of authors' names for this purpose.
 \renewcommand{\shortauthors}{Papachristou}
@@
 
-\noindent \textbf{Method -- } Cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the call graph, provided by Static Graph Analyzers to an augmented graph.
+\noindent \textbf{Method -- } Cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
 Use of the \emph{Louvain Algorithm} to iteratively exhibit its community structure and propose a module--level clustering.
@@
 
-\noindent \textbf{Conclusions --} Semantic information from vector semantics and the call graph can produce 
+\noindent \textbf{Conclusions --} Semantic information from vector semantics as well as the call graph can produce 
 accurate results for software clusterings of large systems.
@@
 architecture viewed from the call graph perspective. 
-We will study Linux codebase and we will compare it with ground truth in using the MoJo metric \cite{mojo} as well as 
-compare it with other state-of-the-art and baseline clustering algorithms \cite{maqbool_overview, evaluation} in terms of 
-\emph{stability}, \emph{authoritativeness} and \emph{extremity}
+We will study the Linux codebase and we will compare it with ground truth in using the MoJo measure \cite{mojo} as well as 
+compare it with other state-of-the-art and baseline clustering algorithms  in terms of \emph{stability}, \emph{authoritativeness} and \emph{extremity}
+\cite{maqbool_overview, evaluation}.
 
@@
 First of all, we tokenize the code and remove the stop-words. 
-After that, for each token, we split it into its constituent parts using dynamic programming and lemmatize 
+After that, for each token, we split it into its constituent parts using dynamic programming \cite{wordninja} and lemmatize 
 each individual sub-token. 
@@
 The codebase is processed by a Static Graph Analyzer. 
-In our approach, focusing on C projects, we use \emph{CScout} \cite{cscout} in order to generate the directed call graph. 
+In our approach, focusing on C projects, we use \emph{CScout} \cite{cscout} in order to generate the directed call graph through function calls between the files. 
 Each source code file is assigned to a module. 
@@
 consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
-and Ward-Linkage \cite{ward} as well as ACDC and LIMBO with $B = 100$, $S = \infty$ and Bag-of-Words features. The results are presented in Table \ref{tab:evaluation}. 
+and Ward-Linkage \cite{ward} using the same document embeddings
+as well as ACDC with structural information \cite{acdc} and LIMBO \cite{limbo} with $B = 100$, $S = \infty$ and Bag-of-Words features. The results are presented in Table \ref{tab:evaluation}. 
 As ground truth we have used the first level directories as a target clustering and as input we have considered 
@@
 and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. 
-As a clustering distance metric we have used the MoJo metric, as proposed in reference \cite{mojo}. 
+As a clustering distance measure we have used the MoJo distance measure, as proposed in reference \cite{mojo}. 
 Since, Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
@@
 
-In Table \ref{tab:evaluation}, there are the results of the clusterings ordered in increasing MoJo distance 
+In Table \ref{tab:evaluation}, we present the results of the clusterings ordered in increasing MoJo distance 
 with respect to the Ground Truth. 
@@
 Our quality metrics for the clusterings are 
-\emph{extremity}, \emph{authoritativeness} and \emph{stability} as proposed in reference \cite{evaluation}
+\emph{extremity}, \emph{authoritativeness} and \emph{stability} as proposed in reference \cite{evaluation}.
 
-Firstly, our approach produced balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, 
-producing an amount of clusters that was close to the Ground Truth with smaller standard deviation in the cluster sizes than 
+Firstly, our approach produces balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, 
+producing a number of clusters that was close to the Ground Truth with smaller standard deviation in the cluster sizes than 
 the other clustering methods, without knowing the number of clusters \emph{a priori}. 
-Besides this, our approach also seems to give balanced clusters with respect to \emph{Median Cluster} criterion. 
-Note that ACDC, which took into account only the structural properties of the files, produced a high 
+Besides this, our approach also gives balanced clusters with respect to \emph{Median Cluster} criterion. 
+Note that ACDC, which takes into account only the structural properties of the files, produced a high 
 granularity clustering that failed to catch the structure of Linux Codebase. 
-Moreover, in the \emph{authoritativeness} criterion, our approach outperformed the other clusterings to a very up to 10 times 
+Moreover, in the \emph{authoritativeness} criterion, our approach outperforms the other clusterings to a very up to 10 times 
 in terms of MoJo distance being very close (smaller is better) to the Ground Truth, with a very small standard deviation. 
@@
 such as ACDC, LIMBO and other Traditional Clustering Algorithms such as Single
-Linkage, Complete Linkage \cite{complete} and Weighted Linkage presenting their efficiency regarding 
+Linkage, Complete Linkage and Weighted Linkage presenting their efficiency regarding 
 multiple feature sets. 
@@
 time, which suggests that semantic-based approached should be followed for gaining better 
-understandings of a software system. Their suggestion is a \emph{term frequency--inverse 
-document frequency} (TF-IDF) model serving as a similarity metric between source code 
+understandings of a software system. Their suggestion in \cite{large_study} is a \emph{term frequency--inverse 
+document frequency} (TF-IDF) model serving as a similarity measure between source code 
 entities. 
@@
 The authors also conducted a study on an older version of  Linux. 
-Moreover, Andritsos and Tzerpos in reference \cite{limbo} present an Information--Theoretic 
+Moreover, Andritsos and Tzerpos in reference \cite{limbo} present an Information-Theoretic 
 approach of SCA by developing LIMBO which clusters modules upon inserting their Distributional Cluster Features 
@@
 Finally, further work is encouraged in several areas such as 
-integration with more static analyzers and use of the project in order to propose layered architectures.
+integration with more static analyzers and use of the project in order to recover layered architectures.
 

### 2019-04-28 manuscript/manuscript.tex
Fix commas

@@
 each individual sub-token. 
-For example the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, 
+For example, the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, 
 \texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.
@@
 \paragraph{Implementation}  
-Our method is implemented in the Python Language using spaCy\cite{spacy} Gensim \cite{gensim} and NetworkX \cite{nx}.
+Our method is implemented in the Python Language using spaCy\cite{spacy}, Gensim \cite{gensim} and NetworkX \cite{nx}.
 
@@
 We have chosen to use Linux as a codebase to evaluate our method on 
-since it is a large and complex system with 27 years of continuous development, spanning 20.3 millions source lines of code (SLOC) at the time of writing.  
+since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (SLOC) at the time of writing.  
 Moreover, it is easy to find ground truth system due to its clear directory structure and construct test-cases for
@@
 As a clustering distance measure we have used the MoJo distance measure, as proposed in reference \cite{mojo}. 
-Since, Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
+Since Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
 multiple times and averaged the results.
@@
 
-\section{Conclusions} This paper is set out to show how we can use a combination of vector semantics
+\section{Conclusions}
+
+This paper is set out to show how we can use a combination of vector semantics
 and information from the call graph in order to produce meaningful clusterings of a software system.
@@
 in terms of \emph{extremity}, \emph{authoritativeness} and \emph{stability} 
-without knowing the number of clusters of the Ground Truth. This evidence strongly
+without even knowing the number of clusters of the Ground Truth. This evidence strongly
 supports the further usage of vector semantics and the call graph for architecture recovery.

### 2019-05-10 manuscript/manuscript.tex
Refactoring

@@
 
-\noindent \textbf{Purpose -- } Propose a method to determine a software's modules without 
+\noindent \textbf{Purpose -- } Propose a novel method to determine a software's modules without 
 knowledge of its architectural structure, and empirically validate the method's performance.
@@
 \noindent \textbf{Method -- } Cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
-Use of the \emph{Louvain Algorithm} to iteratively exhibit its community structure and propose a module--level clustering.
+Use of the \emph{Louvain Algorithm} to determine its community structure and propose a module--level clustering.
 
@@
 
-\noindent \textbf{Conclusions --} Semantic information from vector semantics as well as the call graph can produce 
+\noindent \textbf{Conclusions and Contributions --} Semantic information from vector semantics as well as the call graph can produce 
 accurate results for software clusterings of large systems.
@@
 
-%Modern software systems usually span hundreds of thousands of source code lines (SLOC) 
+%Modern software systems usually span hundreds of thousands of source code lines (\textsc{sloc}) 
 %since the inherent complexity of modern applications that computers have to solve has 
@@
 In modern software systems, the need for adoption of modular software architectural schemata 
-becomes inevitable for robust maintainability of the overall software system.
-Since the architecture of a software system is the most fundamental realization of a 
+becomes inevitable for robust maintainability of their codebases.
+Since the architecture of a software system is the most fundamental realization of the 
 software system, when there is no description of the architecture of it, software 
-architects usually make attempts to recover it. In the past, there have been attempts to 
+architects make attempts to recover it. In the past, methods have been proposed 
 identify the main components of a software system using hierarchical clustering 
 algorithms \cite{maqbool_overview, limbo} mainly by clustering modules into subsystems, given 
-its source code.    
-The possibilities offered by machine learning techniques and practices in the Natural Language Processing (NLP) 
+using the source code.    
+Recently, the possibilities offered by machine learning techniques and practices in the Natural Language Processing (\textsc{nlp}) 
 can also be applied on codebases as corpora of text, thus enabling 
-the extraction of useful information for the semantics of the source codebase 
-inaugurating new modes of reviewing large amounts of source code.
-An example is demonstrated through the Deep Code Search Project \cite{deepcodesearch} .
+the extraction of useful information for the semantics of the source code 
+inaugurating new modes of reviewing the codebase.
 
-This paper aims to propose software clusterings using a combination of vector semantics on the source code provided 
-by \emph{Doc2Vec} as well as the existing structure of 
-the codebase via the call graph in order to form communities and arrive at a module-level 
-architecture viewed from the call graph perspective. 
-We will study the Linux codebase and we will compare it with ground truth in using the MoJo measure \cite{mojo} as well as 
+Our motivation, through this paper, is to use new features, vector semantics and structural information via the call graph in order to perform community detection and arrive at module-level clusterings.
+We will study the Linux codebase and we will compare it with ground truth  using the MoJo measure \cite{mojo} as well as 
 compare it with other state-of-the-art and baseline clustering algorithms  in terms of \emph{stability}, \emph{authoritativeness} and \emph{extremity}
@@
 \begin{table*}
-  \caption{Experimental Results for Linux 4.21 Codebase}
+  \caption{Experimental Results for Linux 4.21}
     \label{tab:evaluation}
@@
     \toprule
-    Algorithm & Number of Clusters & Cluster Size Range & Avg. Cluster & Standard Deviation & Median Cluster & MoJo Distance \\
+    Algorithm & \# Clusters & Size Range & $\bar x$ & $\sigma$ & Median & MoJo Distance \\
     \midrule
-    ACDC \cite{acdc} & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
-    Average Linkage \cite{average} & 21 & 1--3406 & 163 & 725 & 1 & 2092 \\
-    Complete Linkage \cite{complete} & 21 & 1--1529 & 163 & 412 & 19.0 & 1710 \\
-    LIMBO \cite{limbo} & 21 & 50--1810 & 163 & 375 & 50  & 1482 \\
+    \textsc{acdc} \cite{acdc} & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
+    Average Linkage \cite{average} & \emph{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
+    Complete Linkage \cite{complete} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
+    \textsc{limbo} \cite{limbo} & \emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
 
-    Ward Linkage \cite{ward} & 21 & 21--948 & 163 & 223 & 70 & 1138 \\
+    Ward Linkage \cite{ward} & \emph{21} & 21--948 & 163 & 223 & 70 & 1138 \\
 
-    SADE & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
-    SADE (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
+    \textsc{sade} & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
+    \textsc{sade} (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
     \midrule
@@
 
-For the prepossessing stage use the NLP package spaCy \cite{spacy} which provided us with very useful tools for the extraction. 
+For the prepossessing stage we use the \textsc{nlp} package spaCy \cite{spacy} which provided us with very useful tools for preprocessing. 
 After prepossessing, we use Gensim \cite{gensim} to train the Doc2Vec model. 
@@
 The input to the clustering procedure
-is the call graph with cosine similarities of the various modules as weights, thus forming a
-weighted directed graph. Then we run the Louvain Clustering Algorithm \cite{louvain} in
+is the call graph with cosine similarities of the modules as edge weights.
+Then we run the Louvain Clustering Algorithm \cite{louvain} in
 order to obtain the software clustering via maximizing the modularity function with a greedy approach. 
-In case we want to use edge directionality we do a bipartite transformation, detect communities and
-merge the results with a disjoint-set data structure.
+In case we want to consider edge directionality, we do a bipartite transformation, detect communities and
+merge the results with a disjoint-set data structure as stated in reference \cite{malliaros}.
 
 \paragraph{Implementation}  
-Our method is implemented in the Python Language using spaCy\cite{spacy}, Gensim \cite{gensim} and NetworkX \cite{nx}.
+Our method is implemented in the Python Language using spaCy\cite{spacy}, Gensim \cite{gensim} and NetworkX \cite{nx} and is named \textsc{sade}.
+The source code and data are available in \cite{source_code} and \cite{call_graph}.
 
@@
 We have chosen to use Linux as a codebase to evaluate our method on 
-since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (SLOC) at the time of writing.  
+since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (\textsc{sloc}) at the time of writing.  
 Moreover, it is easy to find ground truth system due to its clear directory structure and construct test-cases for
@@
 
-\paragraph{Experimental Setting} Our method was run on Linux 4.21,
-consisting of 20.3 million SLOC against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
+\paragraph{Experimental Setting} Our method was tested on Linux 4.21,
+consisting of 20.3 million \textsc{sloc} against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
 and Ward-Linkage \cite{ward} using the same document embeddings
-as well as ACDC with structural information \cite{acdc} and LIMBO \cite{limbo} with $B = 100$, $S = \infty$ and Bag-of-Words features. The results are presented in Table \ref{tab:evaluation}. 
-As ground truth we have used the first level directories as a target clustering and as input we have considered 
+as well as \textsc{acdc} with structural information \cite{acdc} and \textsc{limbo} \cite{limbo} with $B = 100$, $S = \infty$ and Bag-of-Words features.
+The results are presented in Table \ref{tab:evaluation} and user-defined parameters are formatted in italics.
+As ground truth, we have used the first level directories as a target clustering and as input we have considered 
 the modules of the one-top directories. 
@@
 and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}. 
-As a clustering distance measure we have used the MoJo distance measure, as proposed in reference \cite{mojo}. 
+The MoJo distance measure which counts the minimum number of operations to transform one clustering to another.  
 Since Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
 multiple times and averaged the results. 
+The experimentation with a large and complex system may constitute a threat to our findings' validity since the results are not general.
 
@@
 In Table \ref{tab:evaluation}, we present the results of the clusterings ordered in increasing MoJo distance 
-with respect to the Ground Truth. 
+with respect to the ground truth. 
 We have included the number of clusters produced, the cluster size range, the average cluster size the standard
 deviation in the cluster sizes, the median cluster and the MoJo distances with respect to the ground truth. 
-The Ground Truth clustering is also present in the table. 
+The ground truth clustering is also present in the table. 
 Our quality metrics for the clusterings are 
@@
 Firstly, our approach produces balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, 
-producing a number of clusters that was close to the Ground Truth with smaller standard deviation in the cluster sizes than 
+producing a number of clusters that is close to the ground truth with smaller standard deviation in the cluster sizes than 
 the other clustering methods, without knowing the number of clusters \emph{a priori}. 
 Besides this, our approach also gives balanced clusters with respect to \emph{Median Cluster} criterion. 
-Note that ACDC, which takes into account only the structural properties of the files, produced a high 
-granularity clustering that failed to catch the structure of Linux Codebase. 
-Moreover, in the \emph{authoritativeness} criterion, our approach outperforms the other clusterings to a very up to 10 times 
-in terms of MoJo distance being very close (smaller is better) to the Ground Truth, with a very small standard deviation. 
-This also suggests great \emph{stability} in the resulting clusterings. 
-Note that the other clustering methods we compared against ours gave disappointing MoJo distances even with their cluster
-number defined equal to the one of the Ground Truth.
+Note that \textsc{acdc}, which takes into account only the structural properties of the files, produced a high 
+granularity clustering that failed to catch the structure of Linux. 
+In the \emph{authoritativeness} criterion, our approach outperforms the other clusterings
+in terms of MoJo distance being very close (smaller is better) to the ground truth, with small standard deviation, posing great \emph{stability} in the resulting clusterings. 
+Note that the other clustering methods gave disappointing MoJo distances even with a fixed number of clusters.
 
@@
 Onaiza Maqbool and Haroon A. Babri \cite{maqbool_overview} present an
-overview of the various approaches taken towards to hierarchical clustering algorithms
-for software systems. In their study, they compare the various clustering algorithms
-such as ACDC, LIMBO and other Traditional Clustering Algorithms such as Single
+overview of the various approaches taken towards hierarchical clustering algorithms
+for software systems. In their study, they compare many clustering algorithms
+such as \textsc{acdc}, \textsc{limbo} and other Traditional Clustering Algorithms such as Single
 Linkage, Complete Linkage and Weighted Linkage presenting their efficiency regarding 
@@
 \cite{large_study} reveals significant aspects of a software system and its change over 
-time, which suggests that semantic-based approached should be followed for gaining better 
-understandings of a software system. Their suggestion in \cite{large_study} is a \emph{term frequency--inverse 
-document frequency} (TF-IDF) model serving as a similarity measure between source code 
-entities. 
-Work in Software Clustering Algorithms (SCA) has been extensively done by Tzerpos in
-references \cite{mojo}, \cite{stability}, \cite{acdc} and \cite{limbo} with the ACDC
-and LIMBO clustering algorithms.
+time, which suggests that semantic-based approaches should be followed for gaining better 
+understandings of a software system.
 
-In particular, the ACDC algorithm leans toward to software components comprehension 
+%Their suggestion in \cite{large_study} is a \emph{term frequency--inverse 
+% document frequency} (TF-IDF) model serving as a similarity measure between source code 
+% entities. 
+Work in Software Clustering Algorithms (\textsc{sca}) has been extensively done by many authors in
+references \cite{mojo}, \cite{stability}, \cite{acdc} and \cite{limbo} with the \textsc{acdc}
+and \textsc{limbo} clustering algorithms. 
+In particular, the \textsc{acdc} algorithm leans toward to software components comprehension 
 based on subsystem patterns. Their approach considers an initial structure of the system, 
@@
 Moreover, Andritsos and Tzerpos in reference \cite{limbo} present an Information-Theoretic 
-approach of SCA by developing LIMBO which clusters modules upon inserting their Distributional Cluster Features 
+approach of \textsc{sca} by developing \textsc{limbo} which clusters modules upon inserting their Distributional Cluster Features 
 to a B+-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm, merging the 
@@
 in terms of \emph{extremity}, \emph{authoritativeness} and \emph{stability} 
-without even knowing the number of clusters of the Ground Truth. This evidence strongly
+without even knowing the number of clusters of the ground truth. This evidence 
 supports the further usage of vector semantics and the call graph for architecture recovery.
-Finally, further work is encouraged in several areas such as 
-integration with more static analyzers and use of the project in order to recover layered architectures.
+Finally, as future work we mention the use of this project 
+with more static analyzers, as well as its use to recover layers in layered
+architectural schemata.
 

### 2019-05-10 manuscript/manuscript.tex
Add feature dimension to table.

@@
     \label{tab:evaluation}
-    \begin{tabular}{lrrrrrr}
+    \begin{tabular}{lrrrrrrr}
     \toprule
-    Algorithm & \# Clusters & Size Range & $\bar x$ & $\sigma$ & Median & MoJo Distance \\
+    Algorithm & Feature Dimension & \# Clusters & Size Range & $\bar x$ & $\sigma$ & Median & MoJo Distance \\
     \midrule
-    \textsc{acdc} \cite{acdc} & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
-    Average Linkage \cite{average} & \emph{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
-    Complete Linkage \cite{complete} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
-    \textsc{limbo} \cite{limbo} & \emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
+    \textsc{acdc} \cite{acdc} & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
+    Average Linkage \cite{average} & \emph{300} & \emph{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
+    Complete Linkage \cite{complete} & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
+    \textsc{limbo} \cite{limbo} & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
 
-    Ward Linkage \cite{ward} & \emph{21} & 21--948 & 163 & 223 & 70 & 1138 \\
+    Ward Linkage \cite{ward} & \emph{300} & \emph{21} & 21--948 & 163 & 223 & 70 & 1138 \\
 
-    \textsc{sade} & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
-    \textsc{sade} (Directed) & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
+    \textsc{sade} & \emph{300} & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
+    \textsc{sade} (Directed) & \emph{300} & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
     \midrule
-    Ground Truth & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
+    Ground Truth & -- & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
     \bottomrule

### 2019-06-25 manuscript/manuscript.tex
Remove review template and concatenated abstract

@@
 %%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
-\documentclass[sigconf,review, anonymous]{acmart}
+\documentclass[sigconf]{acmart}
 \usepackage{float}
@@
 \email{papachristoumarios@gmail.com}
+\additionalaffiliation{%
+  \institution{Business Analytics Lab at Athens University of Economics and Business}
+  \streetaddress{Patision Campus}
+  \city{Athens}
+  \state{Attica}
+  \postcode{104 34}
+}
 \affiliation{%
@@
 
-\noindent \textbf{Purpose -- } Propose a novel method to determine a software's modules without 
+In this paper, we propose a novel method to determine a software's modules without 
 knowledge of its architectural structure, and empirically validate the method's performance.
-
-\noindent \textbf{Method -- } Cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
+We cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
 Use of the \emph{Louvain Algorithm} to determine its community structure and propose a module--level clustering.
-
-\noindent \textbf{Results --} Our method performs better in terms of stability, authoritativeness 
+Our method performs better in terms of stability, authoritativeness 
 and extremity over other state-of-the-art clustering methods proposed in literature and is able to decently 
 recover the ground truth clustering of the Linux Kernel. 
-
-\noindent \textbf{Conclusions and Contributions --} Semantic information from vector semantics as well as the call graph can produce 
+Finally, we conclude that semantic information from vector semantics as well as the call graph can produce 
 accurate results for software clusterings of large systems.

### 2019-06-25 manuscript/manuscript.tex
Adjustments according to reviewers' comments

@@
 
+\section{Related Work}
+
+Onaiza Maqbool and Haroon A. Babri \cite{maqbool_overview} present an
+overview of the various approaches taken towards hierarchical clustering algorithms
+for software systems. In their study, they compare many clustering algorithms
+such as \textsc{acdc}, \textsc{limbo} and other Traditional Clustering Algorithms such as Single
+Linkage, Complete Linkage and Weighted Linkage presenting their efficiency regarding 
+multiple feature sets. 
+Added to this, a \emph{semantics-based architectural view} of the system, as discussed in reference
+\cite{large_study} reveals significant aspects of a software system and its change over 
+time, which suggests that semantic-based approaches should be followed for gaining better 
+understandings of a software system.
+
+Work in Software Clustering Algorithms (\textsc{sca}) has been extensively done by many authors in
+references \cite{mojo}, \cite{stability}, \cite{acdc} and \cite{limbo} with the \textsc{acdc}
+and \textsc{limbo} clustering algorithms. 
+In particular, the \textsc{acdc} algorithm leans toward to software components comprehension 
+based on subsystem patterns. Their approach considers an initial structure of the system, 
+without taking into account semantics, and tries to build comprehensive clusterings of the given ground structure. 
+The authors also conducted a study on an older version of  Linux. 
+Moreover, Andritsos and Tzerpos in reference \cite{limbo} present an Information-Theoretic 
+approach of \textsc{sca} by developing \textsc{limbo} which clusters modules upon inserting their Distributional Cluster Features 
+to a B+-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm.
+
 \section{Method}
@@
   \caption{Experimental Results for Linux 4.21}
+  \small
     \label{tab:evaluation}
@@
     Complete Linkage \cite{complete} & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
-    \textsc{limbo} \cite{limbo} & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
+    \textsc{limbo} ($B=100, \; S = \infty$) \cite{limbo} & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
 
@@
 
-\paragraph{Embeddings}
+\paragraph{Method Overview} The codebase is initially preprocessed and the resulting data is fed into a Skip-Gram model for the initial components, which correspond to nodes in the call graph.
+Next, we add weights between the nodes with the normalized similarity between them.
+Finally, we run the Louvain algorithm to obtain a software clustering.
 
-For the prepossessing stage we use the \textsc{nlp} package spaCy \cite{spacy} which provided us with very useful tools for preprocessing. 
-After prepossessing, we use Gensim \cite{gensim} to train the Doc2Vec model. 
 First of all, we tokenize the code and remove the stop-words. 
 After that, for each token, we split it into its constituent parts using dynamic programming \cite{wordninja} and lemmatize 
-each individual sub-token. 
+each individual sub-token via using the \textsc{nlp} package spaCy \cite{spacy}. 
 For example, the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, 
 \texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.
-
-\paragraph{Call Graph Generation} 
-The codebase is processed by a Static Graph Analyzer. 
+We, then, train a Doc2Vec model using Gensim \cite{gensim}. 
+The codebase is also processed by a Static Graph Analyzer. 
 In our approach, focusing on C projects, we use \emph{CScout} \cite{cscout} in order to generate the directed call graph through function calls between the files. 
@@
 Modules can be user defined or automatically generated by their respective directories at a desired directory tree depth. 
-
-\paragraph{Combining semantics and the Call Graph} 
 The input to the clustering procedure
@@
 
-\paragraph{Implementation}  
 Our method is implemented in the Python Language using spaCy\cite{spacy}, Gensim \cite{gensim} and NetworkX \cite{nx} and is named \textsc{sade}.
@@
 and Ward-Linkage \cite{ward} using the same document embeddings
-as well as \textsc{acdc} with structural information \cite{acdc} and \textsc{limbo} \cite{limbo} with $B = 100$, $S = \infty$ and Bag-of-Words features.
+as well as \textsc{acdc} with structural information \cite{acdc} and \textsc{limbo} \cite{limbo} with Bag-of-Words features.
 The results are presented in Table \ref{tab:evaluation} and user-defined parameters are formatted in italics.
@@
 
-\section{Related Work}
-
-Onaiza Maqbool and Haroon A. Babri \cite{maqbool_overview} present an
-overview of the various approaches taken towards hierarchical clustering algorithms
-for software systems. In their study, they compare many clustering algorithms
-such as \textsc{acdc}, \textsc{limbo} and other Traditional Clustering Algorithms such as Single
-Linkage, Complete Linkage and Weighted Linkage presenting their efficiency regarding 
-multiple feature sets. 
-Added to this, a \emph{semantics-based architectural view} of the system, as discussed in reference
-\cite{large_study} reveals significant aspects of a software system and its change over 
-time, which suggests that semantic-based approaches should be followed for gaining better 
-understandings of a software system.
-
-%Their suggestion in \cite{large_study} is a \emph{term frequency--inverse 
-% document frequency} (TF-IDF) model serving as a similarity measure between source code 
-% entities. 
-Work in Software Clustering Algorithms (\textsc{sca}) has been extensively done by many authors in
-references \cite{mojo}, \cite{stability}, \cite{acdc} and \cite{limbo} with the \textsc{acdc}
-and \textsc{limbo} clustering algorithms. 
-In particular, the \textsc{acdc} algorithm leans toward to software components comprehension 
-based on subsystem patterns. Their approach considers an initial structure of the system, 
-without taking into account semantics, and tries to build comprehensive clusterings of the given ground structure. 
-The authors also conducted a study on an older version of  Linux. 
-Moreover, Andritsos and Tzerpos in reference \cite{limbo} present an Information-Theoretic 
-approach of \textsc{sca} by developing \textsc{limbo} which clusters modules upon inserting their Distributional Cluster Features 
-to a B+-tree variant and then applying the \emph{Agglomerative Information Bottleneck} algorithm, merging the 
-clusters with the minimum mutual information loss together.
-
 \section{Conclusions}
@@
 and information from the call graph in order to produce meaningful clusterings of a software system.
-We conclude that we have outperformed state-of-the-art software clusterings and conventional
+We have outperformed state-of-the-art software clusterings and conventional
 agglomerative clustering algorithms 
@@
 supports the further usage of vector semantics and the call graph for architecture recovery.
-Finally, as future work we mention the use of this project 
-with more static analyzers, as well as its use to recover layers in layered
-architectural schemata.
+Finally, the further development of evaluation policies with users should be taken into account.
 

### 2019-06-26 manuscript/manuscript.tex
Extend future work and change template to sigconf, screen

@@
-%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
-\documentclass[sigconf]{acmart}
+\documentclass[sigconf, screen]{acmart}
 \usepackage{float}
-%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.
 
-%%%% Proceedings format for SIGPLAN conferences 
-% \documentclass[sigplan, anonymous, review]{acmart}
-
-%%%% Proceedings format for SIGCHI conferences
-% \documentclass[sigchi, review]{acmart}
-
-%%%% To use the SIGCHI extended abstract template, please visit
-% https://www.overleaf.com/read/zzzfqvkmrfzn
-
-%
-% defining the \BibTeX command - from Oren Patashnik's original BibTeX documentation.
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
 
-% Rights management information. 
-% This information is sent to you when you complete the rights form.
-% These commands have SAMPLE values in them; it is your responsibility as an author to replace
-% the commands and values with those provided to you when you complete the rights form.
-%
-% These commands are for a PROCEEDINGS abstract or paper.
+%%% If you see 'ACMUNKNOWN' in the 'setcopyright' statement below,
+%%% please first submit your publishing-rights agreement with ACM (follow link on submission page).
+%%% Then please update our instructions page and copy-and-paste the NEW commands into your article.
+%%% Please contact us in case of questions; allow up to 10 min for the system to propagate the information.
+%%%
+%%% The following is specific to ESEC/FSE '19-SRC and the paper
+%%% 'Software Clusterings with Vector Semantics and the Call Graph'
+%%% by Marios Papachristou.
+%%%
+\setcopyright{rightsretained}
+\acmPrice{15.00}
+\acmDOI{10.1145/3338906.3342483}
+\acmYear{2019}
 \copyrightyear{2019}
-\acmYear{2019}
-\setcopyright{acmlicensed}
+\acmISBN{978-1-4503-5572-8/19/08}
+\acmConference[ESEC/FSE '19]{Proceedings of the 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{August 26--30, 2019}{Tallinn, Estonia}
+\acmBooktitle{Proceedings of the 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering (ESEC/FSE '19), August 26--30, 2019, Tallinn, Estonia}
 
-\acmConference[ESEC/FSE 2019]{The 27th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{26--30 August, 2019}{Tallinn, Estonia}
-
-%
-% These commands are for a JOURNAL article.
-%\setcopyright{acmcopyright}
-%\acmJournal{TOG}
-%\acmYear{2018}\acmVolume{37}\acmNumber{4}\acmArticle{111}\acmMonth{8}
-%\acmDOI{10.1145/1122445.1122456}
-
-%
-% Submission ID. 
-% Use this when submitting an article to a sponsored event. You'll receive a unique submission ID from the organizers
-% of the event, and this ID should be used as the parameter to this command.
-%\acmSubmissionID{123-A56-BU3}
-
-%
-% The majority of ACM publications use numbered citations and references. If you are preparing content for an event
-% sponsored by ACM SIGGRAPH, you must use the "author year" style of citations and references. Uncommenting
-% the next command will enable that style.
-%\citestyle{acmauthoryear}
-
-%
-% end of the preamble, start of the body of the document source.
 \begin{document}
@@
 \email{papachristoumarios@gmail.com}
-\additionalaffiliation{%
-  \institution{Business Analytics Lab at Athens University of Economics and Business}
-  \streetaddress{Patision Campus}
-  \city{Athens}
-  \state{Attica}
-  \postcode{104 34}
-}
+%\additionalaffiliation{%
+%  \institution{Business Analytics Lab at Athens University of Economics and Business}
+%  \streetaddress{Patision Campus}
+%  \city{Athens}
+%  \state{Attica}
+%  \postcode{104 34}
+%}
 \affiliation{%
@@
 
-In this paper, we propose a novel method to determine a software's modules without 
-knowledge of its architectural structure, and empirically validate the method's performance.
+In this paper, we propose a novel method to determine a software's modules without knowledge of its architectural structure, and empirically validate the method's performance.
 We cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
@@
 Our method performs better in terms of stability, authoritativeness 
-and extremity over other state-of-the-art clustering methods proposed in literature and is able to decently 
+, and extremity over other state-of-the-art clustering methods proposed in the literature and is able to decently 
 recover the ground truth clustering of the Linux Kernel. 
@@
 software system, when there is no description of the architecture of it, software 
-architects make attempts to recover it. In the past, methods have been proposed 
+architects make attempts to recover it. In the past, methods have been proposed to 
 identify the main components of a software system using hierarchical clustering 
@@
 
-Our motivation, through this paper, is to use new features, vector semantics and structural information via the call graph in order to perform community detection and arrive at module-level clusterings.
+Our motivation, through this paper, is to use new features, vector semantics, and structural information via the call graph in order to perform community detection and arrive at module-level clusterings.
 We will study the Linux codebase and we will compare it with ground truth  using the MoJo measure \cite{mojo} as well as 
@@
 \cite{large_study} reveals significant aspects of a software system and its change over 
-time, which suggests that semantic-based approaches should be followed for gaining better 
-understandings of a software system.
+time, which suggests that semantic-based approaches should be followed for gaining better understandings of a software system.
 
@@
 Finally, we run the Louvain algorithm to obtain a software clustering.
+The overall process is described below.
 
@@
 Each source code file is assigned to a module. 
-Modules can be user defined or automatically generated by their respective directories at a desired directory tree depth. 
+Modules can be user-defined or automatically generated by their respective directories at a desired directory tree depth. 
 The input to the clustering procedure
@@
 \paragraph{Decision Rationale for Evaluation System} 
-We have chosen to use Linux as a codebase to evaluate our method on 
-since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (\textsc{sloc}) at the time of writing.  
+We have chosen to use Linux as a codebase to evaluate our method on since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (\textsc{sloc}) at the time of writing.
 Moreover, it is easy to find ground truth system due to its clear directory structure and construct test-cases for
@@
 The results are presented in Table \ref{tab:evaluation} and user-defined parameters are formatted in italics.
-As ground truth, we have used the first level directories as a target clustering and as input we have considered 
+As ground truth, we have used the first level directories as a target clustering and as input, we have considered 
 the modules of the one-top directories. 
@@
 The MoJo distance measure which counts the minimum number of operations to transform one clustering to another.  
-Since Louvain Community Detection produces  different (but very similar) results every time it runs, we ran the simulations 
+Since Louvain Community Detection produces different (but very similar) results from every time it runs, we ran the simulations 
 multiple times and averaged the results. 
@@
 supports the further usage of vector semantics and the call graph for architecture recovery.
-Finally, the further development of evaluation policies with users should be taken into account.
+Finally, the further integration with static analyzers and the development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
 

### 2019-06-28 manuscript/manuscript.tex
Minor grammatical fixes etc.

@@
 
-%%% If you see 'ACMUNKNOWN' in the 'setcopyright' statement below,
-%%% please first submit your publishing-rights agreement with ACM (follow link on submission page).
-%%% Then please update our instructions page and copy-and-paste the NEW commands into your article.
-%%% Please contact us in case of questions; allow up to 10 min for the system to propagate the information.
-%%%
-%%% The following is specific to ESEC/FSE '19-SRC and the paper
-%%% 'Software Clusterings with Vector Semantics and the Call Graph'
-%%% by Marios Papachristou.
-%%%
 \setcopyright{rightsretained}
@@
 \email{papachristoumarios@gmail.com}
-%\additionalaffiliation{%
-%  \institution{Business Analytics Lab at Athens University of Economics and Business}
-%  \streetaddress{Patision Campus}
-%  \city{Athens}
-%  \state{Attica}
-%  \postcode{104 34}
-%}
+\additionalaffiliation{%
+  \institution{Business Analytics Lab at Athens University of Economics and Business}
+  \streetaddress{Patision Campus}
+  \city{Athens}
+  \state{Attica}
+  \postcode{104 34}
+}
 \affiliation{%
@@
   \state{Attica}
+  \country{Greece}
   \postcode{157 73}
 }
+\titlenote{The research described has been carried out as part of the CROSSMINER Project, which has received funding from the European Union's Horizon 2020 Research and Innovation Programme under grant agreement No.
+732223}
 
@@
 We cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
-Use of the \emph{Louvain Algorithm} to determine its community structure and propose a module--level clustering.
+We use the \emph{Louvain Algorithm} to determine its community structure and propose a module--level clustering.
 Our method performs better in terms of stability, authoritativeness 
@@
 
-Our motivation, through this paper, is to use new features, vector semantics, and structural information via the call graph in order to perform community detection and arrive at module-level clusterings.
+Our motivation, through this paper, is to use new features, namely vector semantics, and structural information via the call graph in order to perform community detection and arrive at module-level clusterings.
 We will study the Linux codebase and we will compare it with ground truth  using the MoJo measure \cite{mojo} as well as 
@@
 
-\paragraph{Method Overview} The codebase is initially preprocessed and the resulting data is fed into a Skip-Gram model for the initial components, which correspond to nodes in the call graph.
+The codebase is initially preprocessed and the resulting data is fed into a Skip-Gram model for the initial components, which correspond to nodes in the call graph.
 Next, we add weights between the nodes with the normalized similarity between them.
@@
 
-\paragraph{Decision Rationale for Evaluation System} 
 We have chosen to use Linux as a codebase to evaluate our method on since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (\textsc{sloc}) at the time of writing.
-Moreover, it is easy to find ground truth system due to its clear directory structure and construct test-cases for
+Moreover, its ground truth is is easy to due to the clear directory structure and construct test-cases for
 evaluations. 
@@
 
-\paragraph{Experimental Setting} Our method was tested on Linux 4.21,
+ Our method was tested on Linux 4.21,
 consisting of 20.3 million \textsc{sloc} against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} 
@@
 and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}.
-The MoJo distance measure which counts the minimum number of operations to transform one clustering to another.  
 Since Louvain Community Detection produces different (but very similar) results from every time it runs, we ran the simulations
@@
 
-Firstly, our approach produces balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, 
+Our approach produces balanced clusterings thus demonstrating low \emph{extremity} compared to the other clusterings, 
 producing a number of clusters that is close to the ground truth with smaller standard deviation in the cluster sizes than 
 the other clustering methods, without knowing the number of clusters \emph{a priori}. 
-Besides this, our approach also gives balanced clusters with respect to \emph{Median Cluster} criterion. 
+Besides this, it gives balanced clusters with respect to \emph{Median Cluster} criterion. 
 Note that \textsc{acdc}, which takes into account only the structural properties of the files, produced a high 
@@
 in terms of MoJo distance being very close (smaller is better) to the ground truth, with small standard deviation, posing great \emph{stability} in the resulting clusterings. 
-Note that the other clustering methods gave disappointing MoJo distances even with a fixed number of clusters.
+Closing, the other clustering methods gave disappointing MoJo distances even with a fixed number of clusters.
 

### 2019-06-29 manuscript/manuscript.tex
Finalize paper for camera-ready submission

@@
 We cluster files by combining document embeddings, generated with the  \emph{Doc2Vec} algorithm, and the \emph{call graph}, provided by Static Graph Analyzers to an augmented graph.
-We use the \emph{Louvain Algorithm} to determine its community structure and propose a module--level clustering.
+We use the \emph{Louvain Algorithm} to determine its community structure and propose a module-level clustering.
 Our method performs better in terms of stability, authoritativeness 
@@
 The codebase is initially preprocessed and the resulting data is fed into a Skip-Gram model for the initial components, which correspond to nodes in the call graph.
-Next, we add weights between the nodes with the normalized similarity between them.
-Finally, we run the Louvain algorithm to obtain a software clustering.
+Next, we add weights between the nodes with the normalized similarity $w(i, j) = \left (1 + \cos(\mathbf d_i, \mathbf d_j) \right ) / 2$ between the embeddings.
+Finally, we run the Louvain algorithm to obtain a clustering.
 The overall process is described below.
 
-First of all, we tokenize the code and remove the stop-words. 
+First of all, we tokenize the source code and remove the stop-words. 
 After that, for each token, we split it into its constituent parts using dynamic programming \cite{wordninja} and lemmatize 
@@
 The input to the clustering procedure
-is the call graph with cosine similarities of the modules as edge weights.
+is the call graph with normalized cosine similarities of the modules as edge weights.
 Then we run the Louvain Clustering Algorithm \cite{louvain} in
@@
 In case we want to consider edge directionality, we do a bipartite transformation, detect communities and
-merge the results with a disjoint-set data structure as stated in reference \cite{malliaros}.
+merge the results with a union-find data structure as stated in reference \cite{malliaros}.
 
@@
 We have chosen to use Linux as a codebase to evaluate our method on since it is a large and complex system with 27 years of continuous development and spanning 20.3 millions source lines of code (\textsc{sloc}) at the time of writing.
-Moreover, its ground truth is is easy to due to the clear directory structure and construct test-cases for
+Moreover, it is easy to establish a ground truth due to its clear
+structure and construct test-cases for
 evaluations. 
@@
 and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}.
-Since Louvain Community Detection produces different (but very similar) results from every time it runs, we ran the simulations
+Since Louvain Community Detection produces different, but very similar, results from every time it runs, we ran the simulations
 multiple times and averaged the results. 

### 2019-07-03 manuscript/slides.tex

\documentclass{beamer}
\usepackage{algpseudocode}
\renewcommand{\vec}{\mathbf}
\usepackage[utf8]{inputenc}
 \usetheme{Boadilla}
 \usepackage{ragged2e}
\justifying
%Information to be included in the title page:
\title{Software Clusterings with Vector Semantics and the Call Graph}
\author[Marios Papachristou]{Marios Papachristou \\ \small \url{papachristoumarios@gmail.com} \\ \small \url{el15101@mail.ntua.gr}}

\institute[BaLab]{BALab, Athens University of Economics and Bussiness \\ National Technical University of Athens \\ Advisor: Prof. Diomidis Spinellis}
\date[ESEC/FSE 2019 SRC]{Student Research Competition \\ ESEC/FSE August 2019 \\ Estonia}

\begin{document}

\frame{\titlepage}

\begin{frame}
\frametitle{Problem Statement}

\begin{itemize}
    \item<1-> The architecture of a software system is the most fundamental realization of it
    \item<2-> When there is no specific definition of it, we can attempt to recover it
    \item<3-> One particular problem is the \textbf{clustering of its components into modules} 
    \item<4-> Many methods exist in literature
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Our motivation}

Our motivation, through this work is to

\begin{enumerate}
    \item<1-> Provide a method for software clusterings through \textbf{vector semantics} and the \textbf{call graph}
    \item<2-> Evaluate our method on the \textbf{Linux Kernel Codebase}

    \item<3-> Compare it against state-of-the-art methods (ACDC \cite{acdc}, LIMBO \cite{limbo}) and agglomerative clustering methods (agglomerative clustering \cite{average, complete, ward}) 
\end{enumerate}

\end{frame}

\begin{frame}[allowframebreaks]
\frametitle{Our approach}

We took a simple approach to the problem
\begin{enumerate}
    \item Define the initial ``grains'' of the system. With the term ``grains'' we can refer e.g. to source files (.c), source (.c) and header (.h) files (combined) as well as one-top directory modules. 
    \item Preprocess the files attributed to the ``grains''
    \item Train a Skip-Gram model (Doc2Vec \cite{doc2vec}) on them and obtain vector representations of the ``grains'' $\vec x_1, \dots, \vec x_n$
    \item Generate the call graphs of the system using a static code analyzer (e.g. CScout \cite{cscout})

    \framebreak
    \item Put weights on the graph minor $H(V, E)$ induced by the ``grains'' as the normalized cosine similarities between them $$w(i, j) = \frac {1 + \cos(\vec x_i, \vec x_j)} 2 \qquad \forall (i, j) \in E(H)$$

    \item Run Louvain Community Detection on $H$ and obtain software clusterings
\end{enumerate}

\end{frame}

\begin{frame}{Preprocessing}

\begin{enumerate}
    \item First the code is tokenized and identifiers are split into their constituent parts using dynamic programming and n-grams. Stop-words are removed.

    \item For example \texttt{zone\_seqlock\_init} becomes \texttt{zone}, \texttt{seqlock}, \texttt{init} and \texttt{inprogress} becomes \texttt{in} and \texttt{progress}

    \item Let $L(m)$ be the cost of the optimal split in the $m$-th character of the identifier. Then

    $$\small L(m) = 
    \begin{cases}
	0 & m = 0 \\
	\min_{n \le \ell \le m - n} \{ L(\ell) + c(\ell, \ell + n) \} & \text{else}

\end{cases}
$$

	\item The resulting tokens are lemmatized using the English Lemmatizer provided by the spaCy \cite{spacy} package

\end{enumerate}

\end{frame}

\begin{frame}{Embeddings}

A Skip-Gram model is trained. The objective of such a model is to maximize the probability that a word appears in a window (context) of size $2k + 1$

$$\frac {1} {N} \sum_{t = k}^{N - k} \log \Pr [w_t \mid w_{t-k}, \dots, w_{t + k}]$$

where

$$\Pr [w_c \mid w_t] = \frac {\exp(s(w_c, w_t))} {\sum_{j = 1}^{V} \exp(s(w_t, j)}$$

We have used Doc2Vec for our training which extends the aforementioned idea to extract document embeddings.

\end{frame}

\begin{frame}{The Linux Kernel Codebase}
    \begin{itemize}
        \item A \textbf{HUGE} codebase consisting of $\sim$20.3 million lines of source code
        \begin{figure}
            \centering
            \includegraphics[scale=0.15]{linux.png}
            \caption{Linux Kernel Codebase Size over time. Source: Reddit}
            \label{fig:linux}
        \end{figure}

        \item Constantly growing
        \item Easy-to-find ground truth for evaluation
    \end{itemize}

\end{frame}

\begin{frame}[allowframebreaks]{Call Graphs}

The call graphs were extracted with CScout \cite{cscout} and are of the following forms

\begin{enumerate}
    \item Macro and Function Call Graph
    \item Control Dependency Graph 
    \item File include Graph
    \item Compile-time Dependency Graph
    \item Data dependency Graph (through globals)

\end{enumerate}

The extraction of the call graphs took $\sim 10$h and required $\sim 32$GB of RAM on a Debian server.

\framebreak

\begin{figure}
    \centering
    \includegraphics[keepaspectratio,width=0.9\paperwidth,                          height=\paperheight]{call_graph.png}
    \caption{Call Graph Example between Kernel one-level directories}
    \label{fig:my_label}
\end{figure}

% TODO How cscout operates?

\end{frame}

\begin{frame}{Preparing the graph for clustering}

\begin{itemize}
    \item The weights assigned to every edge are the normalized cosine similarities
    $$\cos(\vec x_i, \vec x_j) = \frac {\langle \vec x_i, \vec x_j \rangle} {\| \vec x_i \| \| \vec x_j \|}$$
    $$w(i, j) = \frac {1 + \cos(\vec x_i, \vec x_j)} {2} \qquad \forall (i, j) \in E(H)$$

    \item Experiments were run using both the directed and the undirected version of the graph. The directed version of the graph required doing a bipartite transformation \cite{malliaros} where every edge $(i, j)$ was mapped to $\{ i, j' \}$ where $j'$ was a copy of $j \in V$. After community detection, the communities which $j$ and $j'$ belonged to were merged using a union-find data structure.

\end{itemize}

\end{frame}

\begin{frame}[allowframebreaks]{Louvain Community Detection}

\begin{itemize}
    \item The Louvain method for community detection aims to produce communities which maximize the modularity function

    $$Q(H) = \frac {1}{2m} \sum_{(i, j) \in E(H)} \left ( w(i, j) - \frac {k(i) k(j)} {2m} \right )$$

    where $m = \sum_{(i, j) \in E} w(i,j)$ and $k(i) = \sum_{j \in \mathrm{in}(i)} w(i, j)$ .

    \item \textsc{modularity-optimization} is NP-Hard \cite{modularity}.
    \item The Louvain algorithm progresses agglomeratively by checking for each node $i$ where the largest change in $\Delta Q (i, j) $ occurs for each $j$ of its neighboring communities. 
    \framebreak

    \item The change $\Delta Q(i, j)$ in modularity is derived as

    \small {
    $$ \Delta Q = \bigg[ \frac{\Sigma_{in} + 2k_{in} (i)}{2m} - \bigg(\frac{\Sigma_{tot} + k(i)}{2m}\bigg)^2 \bigg]-\bigg[\frac{\Sigma_{in}}{2m} - \bigg(\frac{\Sigma_{tot}}{2m}\bigg)^2-\bigg(\frac{k(i)}{2m}\bigg)^2\bigg] $$
    }

    where $\Sigma_{in}$ is sum of all the weights of the links inside the community $i$ is moving into, $\Sigma_{tot}$ is the sum of all the weights of the links to nodes in the community $i$ is moving into, $k_{in} (i)$ is the sum of the weights of the links between $i$ and other nodes in the community that $i$ is  moving into.

    \item The communities that Louvain Clustering produces

\end{itemize}

\end{frame}

\begin{frame}{The MoJo Clustering Distance}

The MoJo \cite{mojo} metric is a clustering distance metric used for comparing software clusterings. The MoJo distance between two clusterings $\mathcal C_1, \mathcal C_2$ is defined as the minimum number of moves and joins to transform one clustering to another where 
\begin{itemize}
    \item \textbf{Move:} Moving a resource from one cluster to another (that includes moving a resource into a previously nonexistent cluster or creating a new cluster.
    \item \textbf{Join:} Join two clusters into one.
\end{itemize}

$$\textrm{MoJo} (\mathcal C_1, \mathcal C_2) = \min \{ \textrm{mno} (\mathcal C_1, \mathcal C_2), \textrm{mno}(\mathcal C_2, \mathcal C_1) \}$$
    Exact computation is not \textbf{efficient} so a \textbf{heuristic} is proposed.
\end{frame}

\begin{frame}[allowframebreaks]{Agglomerative Clustering}

\begin{block}{Idea}
    In every iteration pick two points/vertices $u$ and $v$ that maximize a linkage function and merge them together.
\end{block}

\begin{block}{Algorithm}

    \begin{algorithmic}
    \Function{AgglomerativeClustering}{$w, L, m, \vec x_1, \dots, \vec x_n$}
        \State $\mathcal C_0 \gets \{ \{\vec x_1, \}, \dots, \{ \vec x_n \}\}$
        \For {$1 \le t \le m$}
            \State $(\hat A, \hat B) \gets \mathrm {argmax}_{A, B \in \mathcal C_{t -1}} L(|A|, |B|, w(A, B)) $
            \State $\mathcal C_t \gets \mathcal C_{t - 1} \setminus \{ \{ \hat A \} , \{  \hat B \} \} \cup \{ \{ \hat A \cup \hat B \} \}$
        \EndFor
        \State \Return $\mathcal C_m$
    \EndFunction
  \end{algorithmic}

\end{block}

\framebreak

Linkage functions vary

\begin{itemize}
    \item Average Linkage $\mathrm{argmax}_{A, B} \frac {w(A, B)}{|A||B|}$
    \item Complete Linkage $\mathrm{argmax}_{a \in A, b \in B} w(a, b)$
    \item Single Linkage $\mathrm{argmin}_{a \in A, b \in B} w(a, b)$
    \item Ward Linkage 
    \item Information Loss (Agglomerative Information Bottleneck Algorithm)
\end{itemize}

The affinity function $w$ can be any distance measure. In our comparison, we have used the cosine distance affinity measure between the document embeddings.

\end{frame}

\begin{frame}{Main Software Clustering Algorithms}

The two main algorithms appearing in literature \cite{maqbool_overview, large_study} are

\begin{itemize}
    \item LIMBO. An Information-Theoretic Clustering Algorithm based on the Agglomerative Information Bottleneck. The initial clusters are put on a B+-tree variant (DCF Tree) and then the leaves of the tree become the input of the Agglomerative Information Bottleneck Algorithm.

    \item ACDC. TODO

\end{itemize}

\end{frame}

\begin{frame}{Evaluation}

    \begin{itemize}
         \item Our method was tested on Linux 4.21, consisting of 20.3 million \textsc{sloc} against Average-Linkage \cite{average}, Complete-Linkage \cite{complete} and Ward-Linkage \cite{ward} using the same document embeddings as well as \textsc{acdc} with structural information \cite{acdc} and \textsc{limbo} \cite{limbo} with Bag-of-Words features. 
         \item As ground truth, we have used the first level directories as a target clustering and as input, we have considered the modules of the one-top directories. 
         \item For example, the source code file \texttt{drivers/net/ieee802154\-/mcr20a.c} has a ground truth value of \texttt{drivers} and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}.
         \item Results are averaged over runs

    \end{itemize}

\end{frame}

\begin{frame}{Results}

    \begin{table}
    \Tiny
    \begin{tabular}{lrrrrrrr}
    \hline
    Alg. & Dim.  & $n_c$ & Range & $\bar x$ & $\sigma$ & Median & Dist. \\
    \hline
    \textsc{acdc}  & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
    Average Linkage  & \emph{300} & \emph{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
    Complete Linkage  & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
    \textsc{limbo}  \footnote{($B=100, \; S = \infty$)} & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\

    Ward Linkage\footnote{Eucledian Affinity} & \emph{300} & \emph{21} & 21--948 & 163 & 223 & 70 & 1138 \\

    \textsc{sade} & \emph{300} & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
    \textsc{sade} (Directed) & \emph{300} & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
    \hline
    Ground Truth & -- & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
    \hline
  \end{tabular}
    \caption{Experimental Results for Linux 4.21. Italics denote manually defined parameters}

\end{table}

\end{frame}

\begin{frame}{Discussion}

\begin{itemize}
    \item Surpass all clustering algorithms in terms of MoJo Distance Metric
    \item Production of balanced clusterings 
    \item Production of stable clusterings 
    \item Results were produced without knowing the number of clusters of the ground truth a priori
    \item Provide a simplistic approach to software clustering combining vector semantics and the call graph
\end{itemize}

\end{frame}

\begin{frame}{Conclusions}

\begin{enumerate}
    \item Use vector semantics and the call graph to produce meaningful clusterings
    \item Performing our study on a very large system (Linux) gives us further insight on the nature of software itself
    \item Outperform state-of-the-art and baseline methods in terms of authoritativeness and extremity
    \item Produce stable and balanced clusterings 
\end{enumerate}

\end{frame}

\begin{frame}{Future Work}

\begin{itemize}
    \item Test our system with various codebases
    \item 
\end{itemize}

\end{frame}

\begin{frame}[allowframebreaks]
\frametitle{References}
\bibliographystyle{plain}
\bibliography{references}
\end{frame}

\begin{frame}{}
  \centering \Large {
  \emph{Thank you!}}
  \texttt{https://github.com/papachristoumarios/sade}
\end{frame}

\end{document}

### 2019-07-03 poster/poster.tex
Initial commit of poster

% Gemini theme
% https://github.com/anishathalye/gemini

\documentclass[final]{beamer}

% ====================
% Packages
% ====================

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[size=custom,width=120,height=72,scale=1.0]{beamerposter}
\usetheme{gemini}
\usecolortheme{gemini}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tikz}
 \usepackage{ragged2e}
\usepackage{pgfplots}
\addtobeamertemplate{block begin}{}{\justifying}  %new code

% ====================
% Lengths
% ====================

% If you have N columns, choose \sepwidth and \colwidth such that
% (N+1)*\sepwidth + N*\colwidth = \paperwidth
\newlength{\sepwidth}
\newlength{\colwidth}
\setlength{\sepwidth}{0.025\paperwidth}
\setlength{\colwidth}{0.3\paperwidth}

\newcommand{\separatorcolumn}{\begin{column}{\sepwidth}\end{column}}

% ====================
% Title
% ====================
\title{Software Clusterings with Vector Semantics and the Call Graph}
\author[Marios Papachristou]{Marios Papachristou}

\institute[BaLab]{BALab, Athens University of Economics and Bussiness \\ National Technical University of Athens \\ Advisor: Prof. Diomidis Spinellis}
\date[ESEC/FSE 2019 SRC]{Student Research Competition \\ ESEC/FSE August 2019 \\ Estonia}

% ====================
% Body
% ====================

\begin{document}

\begin{frame}[t]
\begin{columns}[t]
\separatorcolumn

\begin{column}{\colwidth}

  \begin{alertblock}{ABSTRACT}

  	\textbf{Purpose --}  Propose a method to determine a software’s modules
without knowledge of its structure, and empirically validate the
method’s performance.

	\textbf{Method --} Cluster files by combining \textbf{document embeddings}, generated with the \textbf{Doc2Vec} algorithm, and the \textbf{call graphs}, provided
by Static Graph Analyzers to an \textbf{augmented graph}. Use of the Louvain Algorithm to iteratively exhibit its community structure and propose a module–level clustering.

	\textbf{Results --} Our method performs better in terms of stability, 			authoritativeness and extremity over other state-of-the-art clustering
methods proposed in literature and is able to decently recover the
ground truth clustering of the Linux Kernel.

	\textbf{Conclusions --} Semantic information from vector semantics and
the call graph can produce accurate results for software clusterings
of large systems.
  \end{alertblock}

  \begin{block}{Problem Statement}

	\begin{itemize}
    \item The architecture of a software system is the most fundamental realization of it
    \item When there is no specific definition of it, we can attempt to recover it
    \item One particular problem is the \textbf{clustering of its components into modules} 
    \item Many methods exist in literature such as agglomerative clustering baselines as well as more sophisticated algorithms, like LIMBO and ACDC. 
\end{itemize}

  \end{block}

  \begin{alertblock}{Purpose}

\begin{enumerate}
    \item \textbf{Provide} a method for software clusterings through \textbf{vector semantics} and the \textbf{call graph} to determine software's modules without knowledge of its structure
    \item Empirically validate our method performance on the \textbf{Linux Kernel Codebase}

    \item Compare it against state-of-the-art methods (ACDC \cite{acdc}, LIMBO \cite{LIMBO}) and agglomerative clustering methods (agglomerative clustering \cite{average, complete, ward}) 
\end{enumerate}

  \end{alertblock}

\begin{block}{Related Work}

\begin{itemize}
\justifying

\item Onaiza Maqbool and Haroon A. Babri \cite{maqbool_overview} present an
overview of the various approaches taken towards hierarchical clustering algorithms
for software systems. In their study, they compare many clustering algorithms
such as \textbf{ACDC}, \textbf{LIMBO} and other Traditional Clustering Algorithms such as Single
Linkage, Complete Linkage and Weighted Linkage presenting their efficiency regarding 
multiple feature sets.

\item A \textbf{semantics-based architectural view} of the system, as discussed in reference
\cite{large_study} reveals significant aspects of a software system and its change over 
time, which suggests that semantic-based approaches should be followed for gaining better understandings of a software system.

\item The \textbf{ACDC} algorithm leans toward to software components comprehension 
based on subsystem patterns. Their approach considers an initial structure of the system, 
without taking into account semantics, and tries to build comprehensive clusterings of the given ground structure.

\item Andritsos and Tzerpos in reference \cite{LIMBO} present an Information-Theoretic 
approach of \textbf{sca} by developing \textbf{LIMBO} which clusters modules upon inserting their Distributional Cluster Features 
to a B+-tree variant and then applying the \textbf{Agglomerative Information Bottleneck} algorithm.
\end{itemize}

\end{block}

\end{column}

\separatorcolumn

\begin{column}{\colwidth}

\begin{alertblock}{Our Method}

\heading{Preprocessing of the codebase \& Training a Doc2Vec Model}
First of all, we tokenize the source code and remove the stop-words. 
After that, for each token, we split it into its constituent parts using dynamic programming \cite{wordninja} and lemmatize 
each individual sub-token via using the \textbf{NLP} package spaCy \cite{spacy}. 
For example, the method \texttt{\_\_zone\_seqlock\_init} corresponds to \texttt{zone}, \texttt{seqlock} and \texttt{init}, 
\texttt{inprogress} is split into \texttt{in} and \texttt{progress} and \texttt{literals} becomes \texttt{literal}.
We, then, train a Doc2Vec model using Gensim \cite{gensim}.

\heading{Extracting the Call Graph(s)}

\begin{enumerate}
\item The codebase is also processed by a Static Graph Analyzer. 
In our approach, focusing on C projects, we use \textbf{CScout} \cite{cscout} in order to generate the directed call graph through function calls between the files. 
Each source code file is assigned to a module. 
Modules can be user-defined or automatically generated by their respective directories at a desired directory tree depth.

\item The edges have the normalized cosine similarities as weights $w(i,j) = (1 + \cos(\vec x_i, \vec x_j)) / 2$
\end{enumerate}

\heading{Obtaining a clustering}
Then we run the Louvain Clustering Algorithm \cite{louvain} in
order to obtain the software clustering via maximizing the modularity function with a greedy approach. 
The Louvain Method is a greedy optimization method that maximizes the modularity function of a graph $H(V, E)$

$$Q(H) = \frac {1}{2m} \sum_{(i, j) \in E(H)} \left ( w(i, j) - \frac {k(i) k(j)} {2m} \right )$$

where $m = \sum_{(i, j) \in E} w(i,j)$ and $k(i) = \sum_{j \in \mathrm{in}(i)} w(i, j)$ . In case we want to consider edge directionality, we do a bipartite transformation, detect communities and
merge the results with a union-find data structure as stated in reference \cite{malliaros}.

\heading{Decision Rationale for Evaluation System}

We have chosen to use Linux as a codebase to evaluate our method on since

\begin{enumerate}

\item it is a large and complex system with 27 years of continuous development 
\item it spans $\sim$20.3 million lines of source code at the time of writing
\item  it is easy to establish a ground truth due to its clear structure and construct test-cases for evaluations.

\item it is used in related studies \cite{acdc, evaluation} as a reference system for evaluation

\end{enumerate}

\heading{Ground Truth}
As ground truth, we have used the first level directories as a target clustering and as input, we have considered 
the modules of the one-top directories. 
For example, the source code file \texttt{drivers/net/ieee802154\-/mcr20a.c} has a ground truth value of \texttt{drivers} 
and it is considered under the same module as every \texttt{.c} and \texttt{.h} file under \texttt{drivers/net/ieee802154}.

\heading{Experimental Evaluation}

\begin{itemize}

\item Compare our method against agglomerative clustering baselines (average, complete, and Ward linkage) and state-of-the-art methods (LIMBO and ACDC)
\item Use the MoJo distance metric to calculate the distance between the proposed clustering and ground truth
\item Evaluate clusterings \textbf{stability}, \textbf{authoritativeness} and \textbf{extremity}

\end{itemize}

\end{alertblock}

\end{column}

\separatorcolumn

\begin{column}{\colwidth}

  \begin{block}{Results}

    \begin{table}
      \centering
      \small
\begin{tabular}{lrrrrrrr}
    \toprule
    \textbf{Algorithm} & \textbf{Feat. Dim}  & $n_c$ & \textbf{Range} & $\bar x$ & $\sigma$ & \textbf{Median} & \textbf{MoJo D.} \\
    \midrule
    \textbf{ACDC}  & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
    Average Linkage  & \textbf{300} & \textbf{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
    Complete Linkage  & \textbf{300} & \textbf{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
    \textbf{LIMBO}  ($B=100, \; S = \infty$) & 12317 &\textbf{21} & 50--1810 & 163 & 375 & 50  & 1482 \\

    Ward Linkage & \textbf{300} & \textbf{21} & 21--948 & 163 & 223 & 70 & 1138 \\

    \textbf{SADE} & \textbf{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10) & 243 ($\pm$ 1)  \\
    \textbf{SADE} (Directed) & \textbf{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)  & 237 ($\pm$ 2) \\
    \midrule
    Ground Truth & -- & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
    \bottomrule
  \end{tabular}

      \caption{Experimental Results for Linux Kernel 4.21 Codebase. User-defined parameters are in italics.}
    \end{table}

	\begin{itemize}
		\justifying
    \item \textbf{Surpass} all clustering algorithms in terms of MoJo Distance Metric
    \item Production of \textbf{balanced clusterings}
    \item Production of \textbf{stable clusterings}
    \item Results were produced without knowing the number of clusters of the ground truth a priori
    \item Provide a \textbf{simplistic approach} to software clustering combining vector semantics and the call graph
	\end{itemize}

  \end{block}

	\begin{alertblock}{Conclusions}
	\begin{enumerate}
	\justifying
    \item Use of vector semantics and the call graph to produce meaningful clusterings
    \item Performing our study on a very large system (Linux) gives us further insight on the nature of software itself
    \item Outperform state-of-the-art and baseline methods in terms of authoritativeness and extremity
    \item Produce stable and balanced clusterings 
\end{enumerate}

	\end{alertblock}

  \begin{block}{References}

    \scriptsize{\bibliographystyle{plain}\bibliography{references}}

  \end{block}

\end{column}

\separatorcolumn
\end{columns}
\end{frame}

\end{document}

### 2019-07-04 poster/poster.tex
Add slides with makefile

@@
 	\begin{itemize}
-    \item The architecture of a software system is the most fundamental realization of it
-    \item When there is no specific definition of it, we can attempt to recover it
-    \item One particular problem is the \textbf{clustering of its components into modules} 
+    \item The architecture of a software system is the most fundamental realization of it.
+    \item When there is no specific definition of it, we can attempt to recover it.
+    \item One particular problem is the \textbf{clustering of its components into modules}. 
     \item Many methods exist in literature such as agglomerative clustering baselines as well as more sophisticated algorithms, like LIMBO and ACDC. 
@@
 \begin{enumerate}
-    \item \textbf{Provide} a method for software clusterings through \textbf{vector semantics} and the \textbf{call graph} to determine software's modules without knowledge of its structure
-    \item Empirically validate our method performance on the \textbf{Linux Kernel Codebase}
+    \item \textbf{Provide} a method for software clusterings through \textbf{vector semantics} and the \textbf{call graph} to determine software's modules without knowledge of its structure.
+    \item Empirically validate our method performance on the \textbf{Linux Kernel Codebase}.
 
-    \item Compare it against state-of-the-art methods (ACDC \cite{acdc}, LIMBO \cite{LIMBO}) and agglomerative clustering methods (agglomerative clustering \cite{average, complete, ward}) 
+    \item Compare it against state-of-the-art methods (ACDC \cite{acdc}, LIMBO \cite{LIMBO}) and agglomerative clustering methods (agglomerative clustering \cite{average, complete, ward}). 
 \end{enumerate}
@@
 \item Andritsos and Tzerpos in reference \cite{LIMBO} present an Information-Theoretic 
-approach of \textbf{sca} by developing \textbf{LIMBO} which clusters modules upon inserting their Distributional Cluster Features 
+approach of Software Clustering Algorithms by developing \textbf{LIMBO} which clusters modules upon inserting their Distributional Cluster Features 
 to a B+-tree variant and then applying the \textbf{Agglomerative Information Bottleneck} algorithm.
@@
 
-\item The edges have the normalized cosine similarities as weights $w(i,j) = (1 + \cos(\vec x_i, \vec x_j)) / 2$
+\item The edges have the normalized cosine similarities as weights $w(i,j) = (1 + \cos(\mathbf x_i, \mathbf x_j)) / 2$.
 \end{enumerate}
@@
 order to obtain the software clustering via maximizing the modularity function with a greedy approach. 
-The Louvain Method is a greedy optimization method that maximizes the modularity function of a graph $H(V, E)$
+The Louvain Method is a greedy optimization method that (approximately) maximizes the modularity function of a graph $H(V, E)$
 
@@
 
-\item it is a large and complex system with 27 years of continuous development 
-\item it spans $\sim$20.3 million lines of source code at the time of writing
+\item it is a large and complex system with 27 years of continuous development. 
+\item it spans $\sim$20.3 million lines of source code at the time of writing.
 \item  it is easy to establish a ground truth due to its clear structure and construct test-cases for evaluations.
 
-\item it is used in related studies \cite{acdc, evaluation} as a reference system for evaluation
+\item it is used in related studies \cite{acdc, evaluation} as a reference system for evaluation.
 
@@
 
-\item Compare our method against agglomerative clustering baselines (average, complete, and Ward linkage) and state-of-the-art methods (LIMBO and ACDC)
-\item Use the MoJo distance metric to calculate the distance between the proposed clustering and ground truth
-\item Evaluate clusterings \textbf{stability}, \textbf{authoritativeness} and \textbf{extremity}
+\item Compare our method against agglomerative clustering baselines (average, complete, and Ward linkage) and state-of-the-art methods (LIMBO and ACDC).
+\item Use the MoJo distance metric to calculate the distance between the proposed clustering and ground truth.
+\item Evaluate clusterings \textbf{stability}, \textbf{authoritativeness} and \textbf{extremity}.
 
@@
     \textbf{ACDC}  & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
-    Average Linkage  & \textbf{300} & \textbf{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
-    Complete Linkage  & \textbf{300} & \textbf{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
-    \textbf{LIMBO}  ($B=100, \; S = \infty$) & 12317 &\textbf{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
+    Average Linkage  & \emph{300} & \emph{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
+    Complete Linkage  & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
+    \textbf{LIMBO}  ($B=100, \; S = \infty$) & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
 
-    Ward Linkage & \textbf{300} & \textbf{21} & 21--948 & 163 & 223 & 70 & 1138 \\
+    Ward Linkage & \emph{300} & \emph{21} & 21--948 & 163 & 223 & 70 & 1138 \\
 
-    \textbf{SADE} & \textbf{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10) & 243 ($\pm$ 1)  \\
-    \textbf{SADE} (Directed) & \textbf{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)  & 237 ($\pm$ 2) \\
+    \textbf{SADE} & \emph{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10) & 243 ($\pm$ 1)  \\
+    \textbf{SADE} (Directed) & \emph{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)  & 237 ($\pm$ 2) \\
     \midrule
@@
 		\justifying
-    \item \textbf{Surpass} all clustering algorithms in terms of MoJo Distance Metric
-    \item Production of \textbf{balanced clusterings}
-    \item Production of \textbf{stable clusterings}
-    \item Results were produced without knowing the number of clusters of the ground truth a priori
-    \item Provide a \textbf{simplistic approach} to software clustering combining vector semantics and the call graph
+    \item \textbf{Authoritativeness -- } \textbf{Surpass} all clustering algorithms in terms of MoJo Distance Metric.
+    \item \textbf{Extremity -- } Production of \textbf{balanced clusterings}.
+    \item \textbf{Stability -- } Production of \textbf{stable clusterings}.
+    \item Results were produced \textbf{without knowing the number of clusters of the ground truth a priori}.
+    \item Provide a \textbf{simplistic approach} to software clustering combining vector semantics and the call graph.
 	\end{itemize}
@@
 	\justifying
-    \item Use of vector semantics and the call graph to produce meaningful clusterings
-    \item Performing our study on a very large system (Linux) gives us further insight on the nature of software itself
-    \item Outperform state-of-the-art and baseline methods in terms of authoritativeness and extremity
-    \item Produce stable and balanced clusterings 
+    \item Use of \textbf{vector semantics} and the \textbf{call graph} to produce meaningful clusterings.
+    \item Performing our study on a very large system (Linux) gives us \textbf{further insight} on the nature of software itself.
+    \item \textbf{Outperform} state-of-the-art and baseline methods in terms of authoritativeness and extremity.
+    \item Produce \textbf{stable} and \textbf{balanced} clusterings. 
 \end{enumerate}

### 2019-07-04 slides/slides.tex
Add slides with makefile

--- 2019-07-03 manuscript/slides.tex
@@
 \begin{enumerate}
-    \item First the code is tokenized and identifiers are split into their constituent parts using dynamic programming and n-grams. Stop-words are removed.
+    \item<1-> First the code is tokenized and identifiers are split into their constituent parts using dynamic programming and n-grams. Stop-words are removed.
 
-    \item For example \texttt{zone\_seqlock\_init} becomes \texttt{zone}, \texttt{seqlock}, \texttt{init} and \texttt{inprogress} becomes \texttt{in} and \texttt{progress}
+    \item<2-> For example \texttt{zone\_seqlock\_init} becomes \texttt{zone}, \texttt{seqlock}, \texttt{init} and \texttt{inprogress} becomes \texttt{in} and \texttt{progress}
 
-    \item Let $L(m)$ be the cost of the optimal split in the $m$-th character of the identifier. Then
+    %\item Let $L(m)$ be the cost of the optimal split in the $m$-th character of the identifier. Then
 
-    $$\small L(m) = 
-    \begin{cases}
-	0 & m = 0 \\
-	\min_{n \le \ell \le m - n} \{ L(\ell) + c(\ell, \ell + n) \} & \text{else}
+    %$$\small L(m) = 
+    %\begin{cases}
+	%0 & m = 0 \\
+	%\min_{n \le \ell \le m - n} \{ L(\ell) + c(\ell, \ell + n) \} & \text{else}
 
-\end{cases}
-$$
+%\end{cases}
+%$$
 
-	\item The resulting tokens are lemmatized using the English Lemmatizer provided by the spaCy \cite{spacy} package
+	\item<3-> The resulting tokens are lemmatized using the English Lemmatizer provided by the spaCy \cite{spacy} package
 
@@
 
-$$\Pr [w_c \mid w_t] = \frac {\exp(s(w_c, w_t))} {\sum_{j = 1}^{V} \exp(s(w_t, j)}$$
+$$\Pr [w_c \mid w_t] = \frac {\exp(s(w_c, w_t))} {\sum_{j = 1}^{V} \exp(s(w_t, j))}$$
 
@@
 \begin{itemize}
-    \item The weights assigned to every edge are the normalized cosine similarities
+    \item<1-> The weights assigned to every edge are the normalized cosine similarities
     $$\cos(\vec x_i, \vec x_j) = \frac {\langle \vec x_i, \vec x_j \rangle} {\| \vec x_i \| \| \vec x_j \|}$$
@@
 
-    \item Experiments were run using both the directed and the undirected version of the graph.
+    \item<2-> Experiments were run using both the directed and the undirected version of the graph.
 The directed version of the graph required doing a bipartite transformation \cite{malliaros} where every edge $(i, j)$ was mapped to $\{ i, j' \}$ where $j'$ was a copy of $j \in V$.
@@
 \begin{itemize}
-    \item The Louvain method for community detection aims to produce communities which maximize the modularity function
+    \item<1-> The Louvain method for community detection aims to produce communities which maximize the modularity function
 
@@
 
-    \item \textsc{modularity-optimization} is NP-Hard \cite{modularity}.
-    \item The Louvain algorithm progresses agglomeratively by checking for each node $i$ where the largest change in $\Delta Q (i, j) $ occurs for each $j$ of its neighboring communities. 
+    \item<2-> \textsc{modularity-optimization} is NP-Hard \cite{modularity}.
+    \item<3-> The Louvain algorithm progresses agglomeratively by checking for each node $i$ where the largest change in $\Delta Q (i, j) $ occurs for each $j$ of its neighboring communities. 
     \framebreak
 
-    \item The change $\Delta Q(i, j)$ in modularity is derived as
+    \item<4-> The change $\Delta Q(i, j)$ in modularity is derived as
 
@@
 
-    \item The communities that Louvain Clustering produces
+    \item<5-> The communities that Louvain Clustering produces
 
@@
 \begin{itemize}
-    \item \textbf{Move:} Moving a resource from one cluster to another (that includes moving a resource into a previously nonexistent cluster or creating a new cluster.
-    \item \textbf{Join:} Join two clusters into one.
+    \item<1-> \textbf{Move:} Moving a resource from one cluster to another (that includes moving a resource into a previously nonexistent cluster or creating a new cluster.
+    \item<2-> \textbf{Join:} Join two clusters into one.
+	\item<3-> The MoJo distance is therefore defined as
+
+$$\textrm{MoJo} (\mathcal C_1, \mathcal C_2) = \min \{ \textrm{mno} (\mathcal C_1, \mathcal C_2), \textrm{mno}(\mathcal C_2, \mathcal C_1) \}$$
+    \item<4-> Exact computation is not \textbf{efficient} so a \t-extbf{heuristic} is proposed.
+
 \end{itemize}
 
-$$\textrm{MoJo} (\mathcal C_1, \mathcal C_2) = \min \{ \textrm{mno} (\mathcal C_1, \mathcal C_2), \textrm{mno}(\mathcal C_2, \mathcal C_1) \}$$
-    Exact computation is not \textbf{efficient} so a \textbf{heuristic} is proposed.
 \end{frame}
@@
 \begin{itemize}
-    \item Average Linkage $\mathrm{argmax}_{A, B} \frac {w(A, B)}{|A||B|}$
+    \item Average Linkage\footnote{$w(A, B) = \sum_{a \in A, b \in B} w(a,b)$}  $\mathrm{argmax}_{A, B} \frac {w(A, B)}{|A||B|}$
     \item Complete Linkage $\mathrm{argmax}_{a \in A, b \in B} w(a, b)$
@@
 
-    \textsc{sade} & \emph{300} & 10 (\pm 2)  & 2 (\pm 0) -132 (\pm 13) & 64 (\pm 4) & 40 (\pm 4) & 65 (\pm 10) & 243 (\pm 1)  \\
-    \textsc{sade} (Directed) & \emph{300} & 5 (\pm 2) & 1 (\pm 1) - 614 (\pm 1) & 141 (\pm 39) & 253 (\pm 25) & 2 (\pm 0.3)  & 237 (\pm 2) \\
+    \textsc{sade} & \emph{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10) & 243 ($\pm$ 1)  \\
+    \textsc{sade} (Directed) & \emph{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)  & 237 ($\pm$ 2) \\
     \hline
@@
 
-\begin{frame}{Discussion}
+\begin{frame}{Results \& Discussion}
 
 \begin{itemize}
-    \item Surpass all clustering algorithms in terms of MoJo Distance Metric
-    \item Production of balanced clusterings 
-    \item Production of stable clusterings 
-    \item Results were produced without knowing the number of clusters of the ground truth a priori
-    \item Provide a simplistic approach to software clustering combining vector semantics and the call graph
+    \item<1-> Surpass all clustering algorithms in terms of MoJo Distance Metric
+    \item<2-> Production of balanced clusterings 
+    \item<3-> Production of stable clusterings 
+    \item<4-> Results were produced without knowing the number of clusters of the ground truth a priori
+    \item<5-> Provide a simplistic approach to software clustering combining vector semantics and the call graph
 \end{itemize}
@@
 \begin{enumerate}
-    \item Use vector semantics and the call graph to produce meaningful clusterings
-    \item Performing our study on a very large system (Linux) gives us further insight on the nature of software itself
-    \item Outperform state-of-the-art and baseline methods in terms of authoritativeness and extremity
-    \item Produce stable and balanced clusterings 
+    \item<1-> Use \textbf{vector semantics} and the \textbf{call graph} to produce meaningful clusterings
+    \item<2-> Performing our study on a very large system (Linux) gives us further insight on the nature of software itself
+    \item<3-> Outperform state-of-the-art and baseline methods in terms of \textbf{authoritativeness} and \textbf{extremity}
+    \item<4-> Produce \textbf{stable} and \textbf{balanced} clusterings 
 \end{enumerate}
@@
 \begin{itemize}
-    \item Test our system with various codebases
-    \item 
+    \item Testing our system with various codebases to validate method's generalizability
+    \item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
+    \item Integration with more static analyzers 
 \end{itemize}

### 2019-08-12 slides/slides.tex
Clean poster dir

@@
 %Information to be included in the title page:
-\title{Software Clusterings with Vector Semantics and the Call Graph}
+\title[SADE]{Software Clusterings with Vector Semantics and the Call Graph}
 \author[Marios Papachristou]{Marios Papachristou \\ \small \url{papachristoumarios@gmail.com} \\ \small \url{el15101@mail.ntua.gr}}
@@
 
+\usepackage{graphicx}
 \begin{document}
@@
 $$\textrm{MoJo} (\mathcal C_1, \mathcal C_2) = \min \{ \textrm{mno} (\mathcal C_1, \mathcal C_2), \textrm{mno}(\mathcal C_2, \mathcal C_1) \}$$
-    \item<4-> Exact computation is not \textbf{efficient} so a \t-extbf{heuristic} is proposed.
+    \item<4-> Exact computation is not \textbf{efficient} so a \textbf{heuristic} is proposed.
 
@@
 \begin{itemize}
-    \item LIMBO.
-An Information-Theoretic Clustering Algorithm based on the Agglomerative Information Bottleneck.
-The initial clusters are put on a B+-tree variant (DCF Tree) and then the leaves of the tree become the input of the Agglomerative Information Bottleneck Algorithm.
-
-    \item ACDC. TODO
+	\item LIMBO
+	\item ACDC
 
@@
 \begin{itemize}
-    \item Testing our system with various codebases to validate method's generalizability
+    %\item Testing our system with various codebases to validate method's generalizability
     \item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
@@
 \end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Code and Data}
+
+\begin{figure}
+\centering
+\includegraphics[height=0.4\paperheight]{source_and_paper_qr.png} \qquad
+\includegraphics[height=0.4\paperheight]{dataset_qr.png}
+\end{figure}
+
+\centering \Large {
+  \emph{Thank you!}}
+  \url{https://github.com/papachristoumarios/sade}
+  \url{https://zenodo.org/record/2652487}
 
@@
 
-\begin{frame}{}
-  \centering \Large {
-  \emph{Thank you!}}
-  \texttt{https://github.com/papachristoumarios/sade}
-\end{frame}
-
 \end{document}

### 2019-08-23 slides/slides.tex
Update slides

@@
 
-\institute[BaLab]{BALab, Athens University of Economics and Bussiness \\ National Technical University of Athens \\ Advisor: Prof. Diomidis Spinellis}
-\date[ESEC/FSE 2019 SRC]{Student Research Competition \\ ESEC/FSE August 2019 \\ Estonia}
+\institute[BaLab/NTUA]{BALab, Athens University of Economics and Bussiness \\ National Technical University of Athens \\ Advisor: Prof. Diomidis Spinellis}
+\date[ESEC/FSE 2019 SRC]{Student Research Competition \\ ESEC/FSE 2019, Tallin \\ ACAC 2019, Athens}
 
@@
 
-$$\Pr [w_c \mid w_t] = \frac {\exp(s(w_c, w_t))} {\sum_{j = 1}^{V} \exp(s(w_t, j))}$$
+$$\Pr [w_c \mid w_t] = \frac {\exp(s(w_c, w_t))} {\sum_{j = 1}^{V} \exp(s(w_t, j))} \qquad s(w_c, w_t) = \langle \vec d_c, \vec d_t \rangle$$
 
@@
     where $\Sigma_{in}$ is sum of all the weights of the links inside the community $i$ is moving into, $\Sigma_{tot}$ is the sum of all the weights of the links to nodes in the community $i$ is moving into, $k_{in} (i)$ is the sum of the weights of the links between $i$ and other nodes in the community that $i$ is  moving into.
+	\item<5-> This measure determines \textbf{how much the modularity changes via moving (joining) community $i$ with community $j$}.
+At each round, these values are calculated for the community $i$ and its neighboring communities and $i$ is merged with $j^* \in \mathrm{argmax}_{j \in N(i)} \{ \Delta Q(i, j) \}$
 
-    \item<5-> The communities that Louvain Clustering produces
+	\item<6-> Runs in time $O(n \log n)$
 
@@
 The MoJo \cite{mojo} metric is a clustering distance metric used for comparing software clusterings.
-The MoJo distance between two clusterings $\mathcal C_1, \mathcal C_2$ is defined as the minimum number of moves and joins to transform one clustering to another where
+The MoJo distance between two clusterings $\mathcal C_1, \mathcal C_2$ is defined as the \textbf{minimum number of moves and joins} to transform one clustering to another where
 \begin{itemize}
@@
     \item Single Linkage $\mathrm{argmin}_{a \in A, b \in B} w(a, b)$
-    \item Ward Linkage 
+    \item Ward Linkage. Ward minimizes $J(C) = \sum_{\vec x, \vec y \in C} \| \vec x - \vec y \|^2$ for each cluster $C \in \mathcal C$. 
     \item Information Loss (Agglomerative Information Bottleneck Algorithm)
@@
 \begin{itemize}
-	\item LIMBO
-	\item ACDC
+	\item LIMBO: Clusters modules upon inserting their Distributional Cluster
+Features to a B+-tree variant and then applying the Agglomerative
+Information Bottleneck algorithm.\footnote{aka Agglomerative Clustering with Mutual Information Loss as Measure} 
+	\item ACDC: Leans toward to software components comprehension
+based on subsystem patterns.
 
@@
 
-\begin{frame}{Results}
+\begin{frame}[allowframebreaks]
+    \frametitle{Results}
+    \tiny
+    \begin{table}
 
-    \begin{table}
-    \Tiny
     \begin{tabular}{lrrrrrrr}
     \hline
-    Alg. & Dim.  & $n_c$ & Range & $\bar x$ & $\sigma$ & Median & Dist. \\
+    Method & Dim.  & $n_c$ & Range & $\bar x$ & $\sigma$ & Median  \\
     \hline
-    \textsc{acdc}  & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 & 33694\\
-    Average Linkage  & \emph{300} & \emph{21} & 1--3406 & 163 & 725 & 1 & 2092 \\
-    Complete Linkage  & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 & 1710 \\
-    \textsc{limbo}  \footnote{($B=100, \; S = \infty$)} & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50  & 1482 \\
+    \textsc{acdc}  & -- & 9055 & 1 -- 4245 & 5 & 46 & 2 \\
+    Average Linkage  & \emph{300} & \emph{21} & 1--3406 & 163 & 725 & 1 \\
+    Complete Linkage  & \emph{300} & \emph{21} & 1--1529 & 163 & 412 & 19 \\
+    \textsc{limbo}   & 12317 &\emph{21} & 50--1810 & 163 & 375 & 50 \\
 
-    Ward Linkage\footnote{Eucledian Affinity} & \emph{300} & \emph{21} & 21--948 & 163 & 223 & 70 & 1138 \\
+    Ward Linkage & \emph{300} & \emph{21} & 21--948 & 163 & 223 & 70 \\
 
-    \textsc{sade} & \emph{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10) & 243 ($\pm$ 1)  \\
-    \textsc{sade} (Directed) & \emph{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)  & 237 ($\pm$ 2) \\
+    \textsc{sade} & \emph{300} & 10 ($\pm$ 2)  & 2 ($\pm$ 0) -132 ($\pm$ 13) & 64 ($\pm$ 4) & 40 ($\pm$ 4) & 65 ($\pm$ 10)   \\
+    \textsc{sade} (Directed) & \emph{300} & 5 ($\pm$ 2) & 1 ($\pm$ 1) - 614 ($\pm$ 1) & 141 ($\pm$ 39) & 253 ($\pm$ 25) & 2 ($\pm$ 0.3)   \\
     \hline
-    Ground Truth & -- & 21 & 1--1348 & 163 & 341 & 11.0 & -- \\
+    Ground Truth & -- & 21 & 1--1348 & 163 & 341 & 11.0 \\
     \hline
@@
    \caption{Experimental Results for Linux 4.21. Italics denote manually defined parameters}
+
+\end{table}
+
+  \begin{table}
+  \framebreak
+  \small
+  \begin{tabular}{lr}
+    \hline
+    Method &   MoJo Distance \\
+    \hline
+    \textsc{acdc}  &  33694\\
+    Average Linkage  & 2092 \\
+    Complete Linkage  &  1710 \\
+    \textsc{limbo}  \footnote{($B=100, \; S = \infty$) and Bag-of-Words Features} &  1482 \\
+
+    Ward Linkage\footnote{Eucledian Affinity} &  1138 \\
+
+    \textsc{sade} &  243 ($\pm$ 1)  \\
+    \textsc{sade} (Directed) &  237 ($\pm$ 2) \\ \hline
+
+    \end{tabular}
+    \caption{MoJo Distances}
 
@@
 \begin{itemize}
-    %\item Testing our system with various codebases to validate method's generalizability
-    \item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
+    \item Testing our system with various codebases (e.g. gcc, Postgres etc.)
+    %\item Development of evaluation policies with users should be taken into account, especially when dealing with old codebases lacking technical documentation.
     \item Integration with more static analyzers 
+    \item Propose layered software architectures
 \end{itemize}

### 2019-11-29 extended-manuscript/extended-manuscript.tex
Setup outline for extended paper

\documentclass[a4paper, 11pt]{article}
\usepackage[margin=0.7in]{geometry}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage[english]{babel}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\usepackage[colorlinks=true,citecolor=blue,urlcolor=blue]{hyperref}

\usepackage{graphicx}
\renewcommand\vec{\mathbf}

\title{\textbf{Software Clusterings with Vector Semantics and the Call Graph}\footnote{The research described has been carried out as part of the CROSSMINER Project, which has received funding from the European Union's Horizon 2020 Research and Innovation Programme under grant agreement No. 732223}\;\footnote{This work serves as an extended version of \cite{sade}}}

\author{
  Marios Papachristou\footnote{Also affiliated with the National Technical University of Athens} \\
  Business Analytics Lab, AUEB \\
  \texttt{papachristoumarios@gmail.com}
  \and
  Diomidis Spinellis \\
  Business Analytics Lab, AUEB \\
  \texttt{dds@aueb.gr}
}

\date{}

\begin{document}

\maketitle

\section{Introduction}

\section{Method}

\section{Evaluation}

\section{Results and Discussion}

\section{Related Work}

\section{Conclusion}

\newpage

\nocite{*}
\bibliographystyle{alpha}
\bibliography{extended-references}

\end{document}
